---
title: "PARPiCarbo_CH"
author: "Irenaeus Chan"
date: "`r format(Sys.time(), '%a %b %d, %Y %X')`"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_width: 10
    number_sections: false
    theme: cosmo
    df_print: kable
    toc_float:
      collapsed: false
      smooth_scroll: false
  pdf_document:
    toc: true
    toc_depth: '2'
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(cache = TRUE)

library(tidyverse)
library(data.table)
library(readxl)
library(table1)

# Statistics
library(emmeans)
library(afex)
library(rstatix)
library(survival)
library(survminer)

# Plots
library(ggsci)
library(cowplot)
library(ComplexHeatmap)

# Reference
library(BSgenome.Hsapiens.UCSC.hg38)

source("utils/toolbox.R")

data_file_path <- "data/"
figures_save_path <- "figures/"
```

## Load Data
```{r load_data, include=TRUE, message = FALSE, warning = FALSE}
# MSK Impact Data
msk_df <- fread(paste0(data_file_path, "msk_df.minimum.csv"))

# PARP Carbo Data
parp_carbo_df <- fread(paste0(data_file_path, "parp_carbo_df.minimum.tsv"))
timepoints <- fread(paste0(data_file_path, "timepoints.minimum.csv"))
treatment_naive_pre <- fread(paste0(data_file_path, "treatment_naive_pre.csv"))
drug_info <- fread(paste0(data_file_path, "msk_drug_info.csv"))

# MoChA Data
mocha_df <- fread(paste0(data_file_path, "mocha_df.minimum.csv"))
mocha_timepoints <- fread(paste0(data_file_path, "mocha_timepoints.minimum.csv"))

# Demographics
table_demographics <- fread(paste0(data_file_path, "table_demographics.csv"))
mocha_demographics <- fread(paste0(data_file_path, "mocha_sample_demographics.csv"))

# Mouse Data
sheet_names <- excel_sheets(paste0(data_file_path, "CompiledMouseData.xlsx"))
mouse_data <- set_names(map(sheet_names, ~ read_excel(paste0(data_file_path, "CompiledMouseData.xlsx"), .)), sheet_names)

# Mocha Tables for Supplementary Figure 3
ukb_mocha_loh <- read_excel(paste0(data_file_path, "41586_2018_321_MOESM3_ESM.xlsx"))
jpb_mocha_terao <- read_excel(paste0(data_file_path, "41586_2020_2426_MOESM3_ESM.xlsx"))
```

# Check that all Timepoints Variants are IN the Dataframe and vice versa
```{r check_timepoints, include=TRUE, message = FALSE, warning = FALSE}
# All of the timepoint variants exist within the CH calls
setdiff(
    timepoints %>% select(DeID, key, Cohort),
    parp_carbo_df %>% filter(key != "") %>% select(DeID, key, Cohort) %>% distinct()
)
# 13 variants in the timepoints are not in the CH calls because these samples have two separate drug regimens
parp_then_carbo = c('1108236', '1537527', '1592759', '1782310')
carbo_then_parp = c('1536848', '1592606', '1620504', '1734282', '1755649')
# As such, the CH calls will report when the variant was first observed, which is prior to the second drug regimen

setdiff(
    parp_carbo_df %>% filter(key != "") %>% select(DeID, key, Cohort) %>% distinct(),
    timepoints %>% select(DeID, key, Cohort) %>% distinct()
) %>% select(DeID) %>% distinct()
# Some of the called variants came from samples that did not have multiple timepoints
Not_Paired_DEID = c("145068", "1517714", "1547582", "1573250", "1561639", "1627016", "1661003", "1697854", "1728092", "1781724", "1923474", "1931883", "1966221", "2030544", "2057200", "2075647", "2164291", "251740", "863277")
# The rest came from samples that had multiple timepoints, but the analysis window was too narrow to include in the analysis
Samples_Less_Than_30_Days_Apart = c("1651767", "1699017", "1748202", "1795350", "2130036", "390174", "934203")
```

## Pre-defined Variables
```{r pre-defined}
msk_top_10_genes <- c("DNMT3A", "TET2", "PPM1D", "ASXL1", "TP53", "CHEK2", "ATM", "JAK2", "SF3B1", "SRSF2")
gene_list <- c("DNMT3A", "TET2", "ASXL1", "PPM1D", "TP53", "CHEK2", "JAK2", "SF3B1", "SRSF2")
HRD_genes = c('ATM', 'BRCA1', 'BRCA2', 'BRIP1', 'CHEK2', 'RAD51D')
treatment_colors = c('Healthy' = '#BC3C29FF', 'PARPi' = '#E18727FF', 'Carboplatin' = '#0072B2FF')

panel_theme_basic <- theme_bw() + theme(
    panel.border = element_blank(),
    legend.title = element_text(size = 24),
    legend.key.size = unit(5, "mm"),
    legend.text = element_text(size = 24),
    legend.position = "top",
    legend.direction = "horizontal",
    plot.subtitle = element_text(hjust = 0.5, size = 22),
    plot.title = element_text(face = "bold", hjust = 0, vjust = -2, size = 22),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(size = 24),
    axis.text.y = element_text(size = 24),
    axis.text.x = element_text(size = 24),
    axis.title = element_text(size = 26),
    axis.line = element_line(colour = "black"),
    plot.margin = unit(c(0, 0, 0, 0), "pt")
)
```

## Add Germline and Pre-Treatment Status
```{r germline_pre-treatment_status}
timepoints <- timepoints %>%
    select(-HRD) %>%
    left_join(
        table_demographics %>% select(DEID, HRD, HRD_Single),
        by = c("DeID" = "DEID")
    )

# Additional identification of treatment information for each patient
table_demographics <- table_demographics %>%
    left_join(treatment_naive_pre)
```

# Set Reference Variables
```{r reference_variables}
timepoints$Cohort <- factor(timepoints$Cohort, levels = c("Healthy", "Carboplatin", "PARPi"))
timepoints$Gene <- factor(timepoints$Gene, levels = c("TP53", "PPM1D", "CHEK2", "DNMT3A", "TET2", "ASXL1", "SF3B1", "SRSF2", "JAK2"))
timepoints$Drug <- factor(timepoints$Drug, levels = c("No Treatment", "Carboplatin", "Olaparib", "Niraparib", "Rucaparib", "Talazoparib"))   
timepoints$NoTx_Cohort <- factor(timepoints$NoTx_Cohort, levels = c("No Prior Treatment - No Treatment", "Prior Treatment - No Treatment", "No Prior Treatment - Carboplatin", "Prior Treatment - Carboplatin", "No Prior Treatment - PARPi", "Prior Treatment - PARPi"))
timepoints$HRD <- factor(timepoints$HRD, levels = c("No Germline", "HRD Germline", "Other Germline", "Missing"))
timepoints$HRD_Single <- factor(timepoints$HRD_Single, levels = c("No Germline", "ATM", "BRCA1", "BRCA2", "CHEK2", "RAD51D", "Other Germline", "Missing"))

mocha_timepoints$Cohort <- factor(mocha_timepoints$Cohort, levels = c("Healthy", "Carboplatin", "PARPi", "CarboplatinPARPi"))
```

# Figure 1B - Proportion of Mutations per Gene in MSK Data
```{r fig1b, message = FALSE, warning = FALSE, results="hide"}
model_parp_gene <- map_dfr(msk_top_10_genes, function(gene){
    glm(
        formula = as.formula(paste(gene, "~ Treatment")),
        family = binomial(link = "logit"),
        data = msk_df %>% mutate(Treatment = factor(Treatment, levels = c("PARP Inhibitor", "XRT or Systemic Therapy", "No Treatment", "Other Treatment")))
    ) %>%
    sjPlot::get_model_data(type = "est") %>%
    mutate(Gene = gene)
})

fig1b <- map_dfr(msk_top_10_genes, function(gene){
    msk_df %>%
        select(gene, Treatment, ch_pancan_pd) %>%
        group_by(Treatment) %>%
        summarise(n = sum((!!sym(gene) == 1 & ch_pancan_pd == 1), na.rm = TRUE)) %>%
        mutate(Gene = gene)
}) %>%
    left_join(
        msk_df %>%
        group_by(Treatment) %>%
        summarise(total = n()),
        by = "Treatment"
    ) %>%
    mutate(Proportion = n / total) %>%
    mutate(
        Gene = ifelse(Gene %in% c("TP53", "PPM1D", "CHEK2"), paste0("<b>", Gene, "</b>"), paste0(Gene)),
        #Treatment = factor(Treatment, levels = c("PARP Inhibitor", "XRT or Systemic Therapy", "No Treatment", "Other Treatment")),
        Treatment = factor(Treatment, levels = c("No Treatment", "XRT or Systemic Therapy", "PARP Inhibitor", "Other Treatment"))
    ) %>%
    ggplot(
        aes(
            x = reorder(Gene, -Proportion),
            y = Proportion,
            fill = Treatment
        )
    ) +
    geom_bar(color = "black", stat = "identity", position = position_dodge()) +
    labs(
        x = "",
        y = "Percent of Patients with Mutated Gene",
        fill = "Treatment"
    ) +
    panel_theme_basic +
    theme(
        axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1),
        legend.position = c(0.7, 0.75),
        legend.direction = "vertical",
        plot.margin = unit(c(0, 0, 0, 1), "pt")
    ) +
    scale_color_nejm() +
    scale_fill_manual(values = c("No Treatment" = "#BC3C29FF", "PARP Inhibitor" = "#E18727FF", "XRT or Systemic Therapy" = "#0072B2FF")) +
    scale_y_continuous(labels = scales::percent_format(), limits = c(0, 0.17), expand = c(0, 0)) +
    do.call(geom_signif, default_sig(0.12, 1, 1.25, model_parp_gene$p.value[1], model_parp_gene$p.stars[1], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.13, 0.75, 1.25, model_parp_gene$p.value[2], model_parp_gene$p.stars[2], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.06, 3, 3.25, model_parp_gene$p.value[3], model_parp_gene$p.stars[3], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.07, 2.75, 3.25, model_parp_gene$p.value[4], model_parp_gene$p.stars[4], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.14, 2, 2.25, model_parp_gene$p.value[5], model_parp_gene$p.stars[5], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.155, 1.75, 2.25, model_parp_gene$p.value[6], model_parp_gene$p.stars[6], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.08, 4, 4.25, model_parp_gene$p.value[9], model_parp_gene$p.stars[9], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.095, 3.75, 4.25, model_parp_gene$p.value[10], model_parp_gene$p.stars[10], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.03, 5, 5.25, model_parp_gene$p.value[11], model_parp_gene$p.stars[11], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.04, 4.75, 5.25, model_parp_gene$p.value[12], model_parp_gene$p.stars[12], show_values = TRUE, hide_ns = TRUE, textsize = 6))
fig1b
pdf(paste0(figures_save_path, "Figure1B_ProportionMutatedGenes.pdf"), width = 8, height = 8)
fig1b
dev.off()
```

# Figure 1C and 1D - Statistics
```{r fig1cd_stats, message = FALSE, warning = FALSE}
msk_df <- msk_df %>%
    mutate(
        DDR_mut = ifelse(TP53 == 1 | PPM1D == 1 | CHEK2 == 1, 1, 0),
        DDR_CH = ifelse(ch_pancan_pd == 1 & DDR_mut == 1, 1, 0),
        TP53_CH = ifelse(ch_pancan_pd == 1 & TP53 == 1, 1, 0),
        PPM1D_CH = ifelse(ch_pancan_pd == 1 & PPM1D == 1, 1, 0),
        CHEK2_CH = ifelse(ch_pancan_pd == 1 & CHEK2 == 1, 1, 0)
    )

msk_df %>%
    group_by(Treatment) %>%
    summarise(n = sum(DDR_CH, na.rm = TRUE), total = n()) %>%
    mutate(percent = n / total)
    
model_list <- list(
    "Unadjusted" = DDR_CH ~ ind_parp_inhibitor + ind_cytotoxic_therapy + ind_radiotherapy + XRT + ind_immune_therapy + ind_non_parp_targeted_therapy + age + smoke_bin + race_b + timedx_impact,
    "Adjusted for Cytotoxic Therapy" = DDR_CH ~ ind_parp_inhibitor + ind_platinum + ind_topoisomerase_ii_inh + ind_microtubule_damaging + ind_topoisomerase_i_inhi + ind_taxane + ind_antimetabolite + ind_alkylating_agent + ind_radiotherapy + ind_targeted_therapy + XRT + ind_immune_therapy + ind_non_parp_targeted_therapy + age + smoke_bin + race_b + timedx_impact,
    "Adjusted for Amount of Cytotoxic Therapy" = DDR_CH ~ pct_parp_inhibitor + 
      pct_carboplatin + pct_cisplatin + pct_oxaliplatin + pct_anthracycline + pct_epipodophyllotoxins + pct_cytotoxic_therapy_ot + pct_topoisomerase_i_inhi + pct_topoisomerase_ii_inh + 
      pct_microtubule_damaging +  pct_taxane + pct_antimetabolite + pct_alkylating_agent + pct_radiotherapy + pct_targeted_therapy + pct_immune_therapy + 
      eqd_10_t + age + smoke_bin + race_b + timedx_impact
)

msk_models <- map(model_list, function(formula){
    glm(
        formula = formula,
        family = binomial(link = "logit"),
        data = msk_df
    ) %>%
    sjPlot::get_model_data(type = "est")
})
```

# Figure 1C - Logistic Regression Analysis of Therapy on DDR CH Mutations
```{r fig1c, message = FALSE, warning = FALSE, results="hide"}
fig1c <- msk_models$Unadjusted %>%
    filter(str_detect(term, "ind_|XRT")) %>%
    mutate(
        term = case_when(
            term == "ind_parp_inhibitor" ~ "PARP Inhibitor\n(10/54)",
            term == "ind_cytotoxic_therapy" ~ "Cytotoxic Therapy\n(254/4950)",
            term == "ind_radiotherapy" ~ "Radionucleotide Therapy\n(13/160)",
            term == "XRT" ~ "External Beam Radiation\n(133/2217)",
            term == "ind_immune_therapy" ~ "Immune Therapy\n(28/449)",
            term == "ind_non_parp_targeted_therapy" ~ "Other Targeted Therapy\n(90/1736)",
            TRUE ~ term
        ),
        term = factor(term, levels = c("Other Targeted Therapy\n(90/1736)", 
                                    "Immune Therapy\n(28/449)", 
                                    "External Beam Radiation\n(133/2217)", 
                                    "Radionucleotide Therapy\n(13/160)", 
                                    "Cytotoxic Therapy\n(254/4950)", 
                                    "PARP Inhibitor\n(10/54)")),
        p.label = ifelse(p.label == "4.39 ***", "4.4 ***", p.label)
    ) %>%
    ggplot(
        aes(
            x = term,
            y = estimate,
            ymin = conf.low,
            ymax = conf.high,
            col = term,
            fill = term
        )
    ) +
    geom_point(position = position_dodge(width = 0.3), size = 5) +
    geom_errorbar(position = position_dodge(width = 0.3), width = 0.2, linewidth = 1) +
    geom_text(data = . %>% filter(term != "PARP Inhibitor\n(10/54)"), aes_string(label = "p.label", vjust = -0.7), size = 8, position = position_dodge(width = 0.8), color = "black") +
    geom_text(data = . %>% filter(term == "PARP Inhibitor\n(10/54)"), aes(label = p.label, vjust = -0.7), size = 8, position = position_dodge(width = 0.8), color = "black") +
    geom_hline(yintercept = 1, color = "black", linetype = "solid") +
    coord_flip() +
    scale_color_nejm() +
    scale_y_log10(limits = c(0.8, 10), breaks = c(1, 2, 3, 5, 10), labels = scales::label_number(accuracy = 1L)) +
    labs(
        y = "Odds Ratio of DDR CH",
        x = "",
        title = ""
    ) +
    panel_theme_basic +
    theme(
        legend.position = "none",
        #panel.grid.minor = element_line(color = alpha("grey", 0.8), size = 0.5, linetype = "solid"),
        panel.grid.major.x = element_line(color = alpha("grey", 0.8), size = 0.5, linetype = "solid"),
        axis.text.x = ggtext::element_markdown(size = 18),
        #axis.text.y = element_text(size = 18)
    )
fig1c
pdf(paste0(figures_save_path, "Figure1C_Therapy_DDR_CH_OR.pdf"), width = 10, height = 10)
fig1c
dev.off()
```

# Figure 1D - Logistic Regression Analysis of PARP Inhibitor on DDR CH Mutations Adjusted
```{r fig1d, message = FALSE, warning = FALSE, fig.width=16, fig.height=6}
fig1d <- rbind(
        msk_models$`Adjusted for Cytotoxic Therapy` %>% filter(term == "ind_parp_inhibitor"),
        msk_models$`Adjusted for Amount of Cytotoxic Therapy` %>% filter(term == "pct_parp_inhibitor")
    ) %>%
    mutate(
        term = case_when(
            term == "ind_parp_inhibitor" ~ "PARP Inhibitor\n(Adjusted for\nCytotoxic Therapy Class)",
            term == "pct_parp_inhibitor" ~ "PARP Inhibitor\n(Adjusted for\nAmount of Cytotoxic\nTherapy Recieved)"
        ),
        term = factor(term, levels = c("PARP Inhibitor\n(Adjusted for\nAmount of Cytotoxic\nTherapy Recieved)", "PARP Inhibitor\n(Adjusted for\nCytotoxic Therapy Class)")),
        p.label = ifelse(p.label == "2.88 **", "2.9 **", "1.5")
    ) %>%
    ggplot(
        aes(
            x = term,
            y = estimate,
            ymin = conf.low,
            ymax = conf.high,
            col = term,
            fill = term
        )
    ) +
    geom_point(position = position_dodge(width = 0.3), size = 5) +
    geom_errorbar(position = position_dodge(width = 0.3), width = 0.1, size = 1.5) +
    geom_text(aes_string(label = "p.label", vjust = -0.7), size = 8, position = position_dodge(width = 0.8), color = "black") +
    geom_hline(yintercept = 1, color = "black", linetype = "solid") +
    coord_flip() +
    scale_color_manual(values = c("#316675", "#587a8a", "#8badbd")) +
    scale_y_log10(limits = c(0.8, 10), breaks = c(1, 2, 3, 5, 10), labels = scales::label_number(accuracy = 1L)) +
    labs(
        y = "Odds Ratio of DDR CH",
        x = "",
        title = ""
    ) +
    panel_theme_basic +
    theme(
        legend.position = "none",
        #panel.grid.minor = element_line(color = alpha("grey", 0.8), size = 0.5, linetype = "solid"),
        panel.grid.major.x = element_line(color = alpha("grey", 0.8), size = 0.5, linetype = "solid"),
        axis.text.x = ggtext::element_markdown(size = 18),
        #axis.text.y = element_text(size = 18)
    )
fig1d
pdf(paste0(figures_save_path, "Figure1D_Therapy_DDR_CH_Adjusted_OR.pdf"), width = 10, height = 8)
fig1d
dev.off()
```

# Figure 2B - Pre-Treatment VAF Bin Mutation Bar Plot
```{r fig2b, fig.width=7, fig.height=7.6}
df_to_plot <- parp_carbo_df %>%
    filter(average_AF >= 0.002) %>% # Filter out mutations with VAF < 0.2% since these are unlikely to be true positives and would make the plot hard to read
    filter(Gene != "") %>%
    filter(whereincycle == "pre") %>%
    mutate(
        vaf_bin = case_when(
            average_AF < 0.002 ~ "<0.2% VAF",
            average_AF >= 0.002 & average_AF < 0.005 ~ "0.2-0.5% VAF",
            average_AF >= 0.005 & average_AF < 0.01 ~ "0.5-1% VAF", 
            average_AF >= 0.01 & average_AF < 0.05 ~ "1-5% VAF",
            average_AF >= 0.05 ~ ">=5% VAF"
        )
    ) %>%
    group_by(Gene, vaf_bin) %>%
    summarise(n = n()) %>%
    group_by(Gene) %>%
    mutate(
        total = sum(n),
        percentage = (n / total) * 100,
        vaf_bin = factor(vaf_bin, levels = c(">=5% VAF", "1-5% VAF", "0.5-1% VAF", "0.2-0.5% VAF", "<0.2% VAF")),
        Gene = factor(Gene, levels = c(gene_list))
    )

fig2b <- df_to_plot %>%
    ggplot(
        aes(
            x = Gene,
            y = percentage,
            fill = vaf_bin
        )
    ) +
    geom_bar(stat = "identity") +
    labs(
        x = "",
        y = "Percentage of Mutations at Baseline",
        fill = "VAF Bin"
    ) +
    panel_theme_basic +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1, face = "italic"),
        plot.margin = margin(0, 1, 0, 1, "cm"),
        legend.text = element_text(size = 18),
        legend.title = element_blank()
    ) +
    scale_fill_nejm()
fig2b
pdf(paste0(figures_save_path, "Figure2B_VAFBinMutationBarPlot.pdf"), width = 8, height = 8)
fig2b
dev.off()
```

# Figure 2C - Proportion of Mutations per Gene Naive-Treatment
```{r fig2c_naive-treatment, message = FALSE, warning = FALSE, fig.width=15, fig.height=6}
num_mutations_per_person_naive <- parp_carbo_df %>%
    filter(treatment == "No Treatment") %>%
    filter(whereincycle == "pre") %>%   # We want to get the pre-treatment for people without any treatment
    group_by(DeID, Gene) %>%
    summarise(n = sum(putative_driver), .groups = "drop") %>%
    filter(Gene != "") %>%
    pivot_wider(names_from = Gene, values_from = n, values_fill = 0) %>%
    ungroup()

mut_table_naive <- table_demographics %>%
    mutate(treatment_before_pre_sample = ifelse(is.na(treatment_before_pre_sample), manual_classification, treatment_before_pre_sample)) %>%
    filter(treatment_before_pre_sample == "No Treatment") %>%
    left_join(
        num_mutations_per_person_naive,
        by = c("DEID" = "DeID")
    ) %>%
    mutate(
        anytreatment = case_when(
            fromwhere == "G1 Therapeutics" ~ "Treatment",
            fromwhere == "MSK" ~ "Treatment",
            fromwhere == "Carlos" ~ "No Treatment",
            fromwhere == "Ovarian" ~ "Treatment"
        )
    ) %>%
    group_by(DEID, AGE, SEX, RACE, anytreatment) %>%
    summarise_if(is.numeric, function(x) sum(x != 0, na.rm = TRUE))

# Logistic Regression for DDR Mutations
glm(
    data = mut_table_naive %>% mutate(DDR_Mutations = ifelse(PPM1D == 1 | TP53 == 1 | CHEK2 == 1, 1, 0)),
    formula = DDR_Mutations ~ anytreatment + AGE + SEX + RACE,
    family = binomial(link = "logit")
) %>% sjPlot::get_model_data(type = "est")

model_treatment_gene_naive <- map_dfr(gene_list, function(gene){
    print(gene)
    glm(
        data = mut_table_naive,
        formula = as.formula(paste(gene, "~ anytreatment + AGE + SEX + RACE")),
        family = binomial(link = "logit")
    ) %>%
        sjPlot::get_model_data(type = "est") %>%
        mutate(Gene = gene)
})
model_treatment_gene_naive <- model_treatment_gene_naive %>% filter(term == "anytreatmentTreatment")

naive_treatment_prop <- mut_table_naive %>%
    group_by(anytreatment) %>%
    dplyr::select(-AGE, -SEX) %>%
    summarise_if(is.numeric, sum, na.rm = TRUE) %>%
    pivot_longer(cols = -c(anytreatment), names_to = "Gene", values_to = "n") %>%
    group_by(anytreatment, Gene) %>%
    left_join(
        mut_table_naive %>%
            group_by(anytreatment) %>%
            summarise(total_patients = n())
    ) %>%
    mutate(
        Proportion = n / total_patients,
        Gene = factor(Gene, levels = c(gene_list)),
        Treatment = ifelse(anytreatment == "Treatment", "No Genotoxic Treatment", "Untreated"),
        Treatment = factor(Treatment, levels = c("Untreated", "No Genotoxic Treatment"))
    ) %>%
    rowwise() %>%
    mutate(
        # Using exact binomial confidence intervals
        ci_data = list(if(total_patients > 0) {
            binom_test <- binom.test(n, total_patients, conf.level = 0.95)
            tibble(
                lower_ci = binom_test$conf.int[1],
                upper_ci = binom_test$conf.int[2]
            )
        } else {
            tibble(lower_ci = 0, upper_ci = 0)
        }),
        lower_ci = ci_data$lower_ci,
        upper_ci = ci_data$upper_ci
    ) %>%
    select(-ci_data) %>%
    ungroup()
```

# Figure 2C - Proportion of Mutations per Gene Pre-Treatment
```{r fig2c_pre-treatment, message = FALSE, warning = FALSE, fig.width=15, fig.height=6}
num_mutations_per_person_pre <- parp_carbo_df %>%
    filter(whereincycle == "pre") %>%
    group_by(DeID, Gene, anytreatment) %>%
    summarise(n = sum(putative_driver)) %>%
    filter(Gene != "") %>%
    pivot_wider(names_from = Gene, values_from = n, values_fill = 0) %>%
    ungroup()

mut_table_pre <- table_demographics %>%
    left_join(num_mutations_per_person_pre, by = c("DEID" = "DeID")) %>%
    mutate(
        anytreatment = case_when(
            fromwhere == "G1 Therapeutics" ~ "Treatment",
            fromwhere == "MSK" ~ "Treatment",
            fromwhere == "Carlos" ~ "No Treatment",
            fromwhere == "Ovarian" ~ "Treatment"
        )
    ) %>%
    group_by(DEID, AGE, SEX, RACE, anytreatment) %>%
    summarise_if(is.numeric, function(x) sum(x != 0, na.rm = TRUE))

# Logistic Regression for DDR Mutations
glm(
    data = mut_table_pre %>% mutate(DDR_Mutations = ifelse(PPM1D == 1 | TP53 == 1 | CHEK2 == 1, 1, 0)),
    formula = DDR_Mutations ~ anytreatment + AGE + SEX + RACE,
    family = binomial(link = "logit")
) %>% sjPlot::get_model_data(type = "est")

model_treatment_gene_pre <- map_dfr(gene_list, function(gene){
    glm(
        data = mut_table_pre,
        formula = as.formula(paste(gene, "~ anytreatment + AGE + SEX + RACE")),
        family = binomial(link = "logit")
    ) %>%
        sjPlot::get_model_data(type = "est") %>%
        mutate(Gene = gene)
})
model_treatment_gene_pre <- model_treatment_gene_pre %>% filter(term == "anytreatmentTreatment")

pre_treatment_prop <- mut_table_pre %>%
    group_by(anytreatment) %>%
    dplyr::select(-AGE, -SEX) %>%
    summarise_if(is.numeric, sum, na.rm = TRUE) %>%
    pivot_longer(cols = -c(anytreatment), names_to = "Gene", values_to = "n") %>%
    group_by(anytreatment, Gene) %>%
    left_join(
        mut_table_pre %>%
            group_by(anytreatment) %>%
            summarise(total_patients = n())
    ) %>%
    mutate(
        Proportion = n / total_patients,
        Gene = factor(Gene, levels = c(gene_list)),
        Treatment = ifelse(anytreatment == "Treatment", "Pre-Treatment", "Untreated"),
        Treatment = factor(Treatment, levels = c("Untreated", "Pre-Treatment"))
    ) %>%
    rowwise() %>%
    mutate(
        # Using exact binomial confidence intervals
        ci_data = list(if(total_patients > 0) {
            binom_test <- binom.test(n, total_patients, conf.level = 0.95)
            tibble(
                lower_ci = binom_test$conf.int[1],
                upper_ci = binom_test$conf.int[2]
            )
        } else {
            tibble(lower_ci = 0, upper_ci = 0)
        }),
        lower_ci = ci_data$lower_ci,
        upper_ci = ci_data$upper_ci
    ) %>%
    select(-ci_data) %>%
    ungroup()
```

# Figure 2C - Proportion of Mutations per Gene Post-Treatment
```{r fig2c_post-treatment, message = FALSE, warning = FALSE, fig.width=15, fig.height=6}
num_mutations_per_person_post <- parp_carbo_df %>%
    filter(whereincycle == "post") %>%
    group_by(DeID, Gene, anytreatment) %>%
    summarise(n = sum(putative_driver)) %>%
    filter(Gene != "") %>%
    pivot_wider(names_from = Gene, values_from = n, values_fill = 0) %>%
    ungroup()

mut_table_post <- table_demographics %>%
    left_join(num_mutations_per_person_post, by = c("DEID" = "DeID")) %>%
    mutate(
        anytreatment = case_when(
            fromwhere == "G1 Therapeutics" ~ "Treatment",
            fromwhere == "MSK" ~ "Treatment",
            fromwhere == "Carlos" ~ "No Treatment",
            fromwhere == "Ovarian" ~ "Treatment"
        )
    ) %>%
    group_by(DEID, AGE, SEX, RACE, anytreatment) %>%
    summarise_if(is.numeric, function(x) sum(x != 0, na.rm = TRUE))

# Logistic Regression for DDR Mutations
glm(
    data = mut_table_post %>% mutate(DDR_Mutations = ifelse(PPM1D == 1 | TP53 == 1 | CHEK2 == 1, 1, 0)),
    formula = DDR_Mutations ~ anytreatment + AGE + SEX + RACE,
    family = binomial(link = "logit")
) %>% sjPlot::get_model_data(type = "est")

model_treatment_gene_post <- map_dfr(gene_list, function(gene){
    glm(
        data = mut_table_post,
        formula = as.formula(paste(gene, "~ anytreatment + AGE + SEX + RACE")),
        family = binomial(link = "logit")
    ) %>%
        sjPlot::get_model_data(type = "est") %>%
        mutate(Gene = gene)
})
model_treatment_gene_post <- model_treatment_gene_post %>% filter(term == "anytreatmentTreatment")

post_treatment_prop <- mut_table_post %>%
    group_by(anytreatment) %>%
    dplyr::select(-AGE, -SEX) %>%
    summarise_if(is.numeric, sum, na.rm = TRUE) %>%
    pivot_longer(cols = -c(anytreatment), names_to = "Gene", values_to = "n") %>%
    group_by(anytreatment, Gene) %>%
    left_join(
        mut_table_post %>%
            group_by(anytreatment) %>%
            summarise(total_patients = n())
    ) %>%
    mutate(
        Proportion = n / total_patients,
        Gene = factor(Gene, levels = c(gene_list)),
        Treatment = ifelse(anytreatment == "Treatment", "Post-Treatment", "Untreated"),
        Treatment = factor(Treatment, levels = c("Untreated", "Post-Treatment"))
    ) %>%
    rowwise() %>%
    mutate(
        # Using exact binomial confidence intervals
        ci_data = list(if(total_patients > 0) {
            binom_test <- binom.test(n, total_patients, conf.level = 0.95)
            tibble(
                lower_ci = binom_test$conf.int[1],
                upper_ci = binom_test$conf.int[2]
            )
        } else {
            tibble(lower_ci = 0, upper_ci = 0)
        }),
        lower_ci = ci_data$lower_ci,
        upper_ci = ci_data$upper_ci
    ) %>%
    select(-ci_data) %>%
    ungroup()

fig2c <-rbind(
        naive_treatment_prop,
        pre_treatment_prop %>% filter(Treatment == "Pre-Treatment"),
        post_treatment_prop %>% filter(Treatment == "Post-Treatment")
    ) %>%
    mutate(
        Treatment = case_when(
            Treatment == "Untreated" ~ "Healthy Controls",
            Treatment == "No Genotoxic Treatment" ~ "Pre-Treatment with No Prior Genotoxic Therapy",
            Treatment == "Pre-Treatment" ~ "Pre-Carboplatin/PARP Inhibitor Treatment",
            Treatment == "Post-Treatment" ~ "Post-Carboplatin/PARP Inhibitor Treatment"
        ),
        Treatment = factor(Treatment, levels = c("Healthy Controls", "Pre-Treatment with No Prior Genotoxic Therapy", "Pre-Carboplatin/PARP Inhibitor Treatment", "Post-Carboplatin/PARP Inhibitor Treatment"))
    ) %>%
    ggplot(
        aes(
            x = Gene,
            y = Proportion,
            fill = Treatment
        )
    ) +
    geom_bar(color = "black", stat = "identity", position = position_dodge()) +
    labs(
        x = "",
        y = "Percent of Patients with Mutated Gene",
        fill = "Treatment"
    ) +
    panel_theme_basic +
    theme(
        axis.text.y = ggtext::element_markdown(),
        axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1),
        legend.position = c(0.7, 0.8),
        legend.direction = "vertical",
        legend.text = element_text(size = 18),
        plot.margin = margin(2, 0, 0, 1, "cm")
    ) +
    scale_y_continuous(labels = scales::percent, limits = c(0, 0.7), expand = c(0, 0)) +
    scale_fill_nejm() +
    do.call(geom_signif, default_sig(0.65, 0.65, 1.25, model_treatment_gene_post$p.value[1], model_treatment_gene_post$p.stars[1], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.4, 1.65, 2.25, model_treatment_gene_post$p.value[2], model_treatment_gene_post$p.stars[2], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.1, 2.65, 3.25, model_treatment_gene_post$p.value[3], model_treatment_gene_post$p.stars[3], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.45, 3.65, 4.25, model_treatment_gene_post$p.value[4], model_treatment_gene_post$p.stars[4], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.35, 4.65, 5.25, model_treatment_gene_post$p.value[5], model_treatment_gene_post$p.stars[5], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.25, 5.65, 6.25, model_treatment_gene_post$p.value[6], model_treatment_gene_post$p.stars[6], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.1, 6.65, 7.25, model_treatment_gene_post$p.value[7], model_treatment_gene_post$p.stars[7], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.1, 7.65, 8.25, model_treatment_gene_post$p.value[8], model_treatment_gene_post$p.stars[8], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.1, 8.65, 9.25, model_treatment_gene_post$p.value[9], model_treatment_gene_post$p.stars[9], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    # Pre Stuff
    do.call(geom_signif, default_sig(0.55, 0.65, 1.05, model_treatment_gene_pre$p.value[1], model_treatment_gene_pre$p.stars[1], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.3, 1.65, 2.05, model_treatment_gene_pre$p.value[2], model_treatment_gene_pre$p.stars[2], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.1, 2.65, 3.05, model_treatment_gene_pre$p.value[3], model_treatment_gene_pre$p.stars[3], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.4, 3.65, 4.05, model_treatment_gene_pre$p.value[4], model_treatment_gene_pre$p.stars[4], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.3, 4.65, 5.05, model_treatment_gene_pre$p.value[5], model_treatment_gene_pre$p.stars[5], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.2, 5.65, 6.05, model_treatment_gene_pre$p.value[6], model_treatment_gene_pre$p.stars[6], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.05, 6.65, 7.05, model_treatment_gene_pre$p.value[7], model_treatment_gene_pre$p.stars[7], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.05, 7.65, 8.05, model_treatment_gene_pre$p.value[8], model_treatment_gene_pre$p.stars[8], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.05, 8.65, 9.05, model_treatment_gene_pre$p.value[9], model_treatment_gene_pre$p.stars[9], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    # Naive Stuff
    do.call(geom_signif, default_sig(0.65, 0.65, 0.85, model_treatment_gene_naive$p.value[1], model_treatment_gene_naive$p.stars[1], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.4, 1.65, 1.85, model_treatment_gene_naive$p.value[2], model_treatment_gene_naive$p.stars[2], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.2, 2.65, 2.85, model_treatment_gene_naive$p.value[3], model_treatment_gene_naive$p.stars[3], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.3, 3.65, 3.85, model_treatment_gene_naive$p.value[4], model_treatment_gene_naive$p.stars[4], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.35, 4.65, 4.85, model_treatment_gene_naive$p.value[5], model_treatment_gene_naive$p.stars[5], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.25, 5.65, 5.85, model_treatment_gene_naive$p.value[6], model_treatment_gene_naive$p.stars[6], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.1, 6.65, 6.85, model_treatment_gene_naive$p.value[7], model_treatment_gene_naive$p.stars[7], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.1, 7.65, 7.85, model_treatment_gene_naive$p.value[8], model_treatment_gene_naive$p.stars[8], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(0.1, 8.65, 8.85, model_treatment_gene_naive$p.value[9], model_treatment_gene_naive$p.stars[9], show_values = TRUE, hide_ns = TRUE, textsize = 6))
fig2c
pdf(paste0(figures_save_path, "Figure2C_ProportionMutatedGenes.pdf"), width = 12, height = 8)
fig2c
dev.off()
```

# Figure 2D - Average Number of Mutations per Gene Post-Treatment
```{r fig2d, message = FALSE, warning = FALSE, fig.width=18, fig.height=8}
ddr_mut_table <- table_demographics %>%
    left_join(
        # For each person, count the number of mutations in DDR genes
        num_mutations_per_person_post %>%
            mutate(DDR_Mutations = rowSums(across(c(PPM1D, TP53, CHEK2)))) %>%
            select(DeID, DDR_Mutations), 
        by = c("DEID" = "DeID")
    ) %>%
    mutate(
        # If the individual has no mutations, set to 0
        DDR_Mutations = ifelse(is.na(DDR_Mutations), 0, DDR_Mutations),
        anytreatment = case_when(
            fromwhere == "G1 Therapeutics" ~ "Treatment",
            fromwhere == "MSK" ~ "Treatment",
            fromwhere == "Carlos" ~ "Healthy",
            fromwhere == "Ovarian" ~ "Treatment"
        )
    ) %>%
    select(DEID, anytreatment, DDR_Mutations) %>%
    # Limit to max of 5 mutations for visualization purposes
    mutate(
        DDR_Mutations = ifelse(DDR_Mutations >= 5, "5+", as.character(DDR_Mutations)),
        DDR_Mutations = factor(DDR_Mutations, levels = c(as.character(0:4), "5+")),
        anytreatment = factor(anytreatment, levels = c("Healthy", "Treatment"))
    ) %>%
    group_by(DDR_Mutations, anytreatment, .drop = FALSE) %>%
    summarise(number_of_patients = n()) %>%
    ungroup() %>%
    group_by(anytreatment) %>%
    mutate(
        total_patients = sum(number_of_patients), 
        proportion = number_of_patients / total_patients,
    )

fig2d <- ddr_mut_table %>%
    ggplot(
        aes(
            x = DDR_Mutations,
            y = proportion,
            fill = anytreatment
        )
    ) +
    geom_bar(color = "black", stat = "identity", position = position_dodge()) +
    labs(
        x = "Number of DDR Mutations",
        y = "Percent of Patients",
        fill = "Treatment"
    ) +
    panel_theme_basic +
    theme(
        legend.position = c(0.7, 0.6),
        legend.direction = "vertical",
        plot.margin = margin(0, 0, 1, 1, "cm")
    ) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0)) +
    scale_fill_nejm()
fig2d
pdf(paste0(figures_save_path, "Figure2D_AverageNumberMutatedGenes.pdf"), width = 6, height = 8)
fig2d
dev.off()
```

# Figure 2E - Post-Treatment Waterfall Plot
```{r fig2e, fig.width=10, fig.height=8}
df_to_maf <- parp_carbo_df %>% 
    filter(!(DeID %in% c(parp_then_carbo, carbo_then_parp))) %>%    # Remove individuals who received both PARP Inhibitor and Carboplatin to avoid confounding effects in the visualization
    filter(VariantClass != "synonymous_variant", putative_driver == 1, whereincycle == "post") %>%
    filter(key != "") %>%
    separate(key, into = c("Chromosome", "Start_Position", "alleles"), sep = " ") %>%
    separate(alleles, into = c("Reference_Allele", "Tumor_Seq_Allele2"), sep = ">") %>%
    mutate(
        Tumor_Sample_Barcode = DeID,
        Hugo_Symbol = Gene,
        Variant_Classification = VariantClass,
        Start_Position = as.numeric(Start_Position),
        Variant_Type = case_when(
            nchar(Reference_Allele) == nchar(Tumor_Seq_Allele2) ~ "SNP",
            nchar(Reference_Allele) < nchar(Tumor_Seq_Allele2) ~ "INS",
            nchar(Reference_Allele) > nchar(Tumor_Seq_Allele2) ~ "DEL"
        ),
        End_Position = case_when(
            Variant_Type == "SNP" ~ Start_Position,
            Variant_Type == "INS" ~ Start_Position,
            Variant_Type == "DEL" ~ (Start_Position + nchar(Reference_Allele) - 1)
        ),
        stringsAsFactors = FALSE
    )

nejmPal <- pal_nejm("default")(8)
col <- nejmPal[1:6]
names(col) <- c("Multimutation", "Frameshift", "Missense", "Nonsense", "Splicing", "Other")

# Function to define colors for alteration cells
alter_fun_vec <- function(x, y, w, h, v) {
    tmp <- pal_nejm("default")(6)
    names(tmp) <- c("Multimutation", "Frameshift", "Missense", "Nonsense", "Splicing", "Other")
    colNames <- names(v)[!is.na(names(v))]
    v <- matrix(v, ncol = length(colNames))
    color <- apply(v, 1, function(x) {
        if (sum(x) == 0) {
            "#FFFFFF"
        } else {
            tmp[colNames[x]][1]
        }
    })
    grid.rect(x, y, w * 1.1, h,
        gp = gpar(fill = color, col = NA)
    )
}

# Preparing Data for OncoPrint
toPlot <- df_to_maf %>%
    dplyr::select(DeID, Gene, VariantClass, Cohort) %>%
    dplyr::filter(Gene != "") %>%
    group_by(DeID, Gene) %>%
    mutate(VariantClass = ifelse(n() > 1, "multi_mutation", VariantClass)) %>%
    ungroup() %>%
    distinct() %>%
    mutate(
        VariantClass = case_match(
            VariantClass,
            "multi_mutation" ~ "Multimutation",
            "frameshift_variant" ~ "Frameshift",
            c("missense_variant", "inframe_deletion", "inframe_insertion") ~ "Missense",
            "splice_region_variant" ~ "Splicing",
            c("start_lost", "stop_gained") ~ "Nonsense",
            .default = "Other"
        )
    )

# Creating Matrix for OncoPrint
mat <- toPlot %>%
    dplyr::select(DeID, Gene, VariantClass) %>%
    pivot_wider(names_from = DeID, values_from = VariantClass, values_fill = "") %>%
    column_to_rownames("Gene")
# Ordering rows by number of mutations per gene
rowOrder <- toPlot %>%
    group_by(Gene) %>%
    summarise(n = n()) %>%
    arrange(desc(n)) %>%
    pull(Gene) %>%
    unique()
# Ordering columns by Cohort, Gene, VariantClass, and number of mutations
colOrder <- toPlot %>%
    group_by(DeID) %>%
    mutate(n = sum(VariantClass != "")) %>%
    ungroup() %>%
    arrange(
        factor(Cohort, levels = c("Healthy", "Carboplatin", "PARPi")),
        factor(Gene, levels = rowOrder),
        factor(VariantClass, levels = c("Multimutation", "Frameshift", "Missense", "Nonsense", "Splicing", "Other")),
        desc(n)
    ) %>%
    pull(DeID) %>%
    unique()
# Reordering matrix
mat <- mat[rowOrder, colOrder]
# Creating Column Information for Annotations
colInfor <- toPlot %>%
    dplyr::select(DeID, Cohort) %>%
    distinct() %>%
    arrange(factor(DeID, levels = colOrder))

p <- oncoPrint(mat,
    alter_fun = alter_fun_vec,
    alter_fun_is_vectorized = TRUE,
    col = col,
    row_order = rownames(mat),
    column_order = colnames(mat),
    show_pct = TRUE,
    pct_side = "right",
    row_names_side = "left",
    top_annotation = HeatmapAnnotation(
        annotation_name_gp = gpar(fontsize = 10),
        annotation_name_side = "left",
        annotation_name_rot = 90,
        annotation_name_offset = unit(15, "points"),
        "# of Muts" = anno_oncoprint_barplot() %>%
            {
                x <- .
                x@show_name <- TRUE
                x
            }
    ),
    right_annotation = rowAnnotation(
        annotation_name_gp = gpar(fontsize = 10),
        annotation_name_side = "top",
        annotation_name_offset = unit(15, "points"),
        "# of Samples" = anno_oncoprint_barplot() %>%
            {
                x <- .
                x@show_name <- TRUE
                x
            }
    ),
    bottom_annotation = HeatmapAnnotation(
        Cohort = colInfor$Cohort,
        col = list(
            Cohort = c(`Healthy` = nejmPal[1], `Carboplatin` = nejmPal[2], `PARPi` = nejmPal[3])
        ),
        annotation_legend_param = list(
            Cohort = list(
                nrow = 1,
                at = c("Healthy", "Carboplatin", "PARPi")
            )
        )
    ),
    heatmap_legend_param = list(
        title = "Alteration",
        nrow = 2,
        by_row = TRUE,
        at = c("Multimutation", "Frameshift", "Missense", "Nonsense", "Splicing", "Other")
    )
)

pdf(paste0(figures_save_path, "Figure2E_WaterfallPlot.pdf"), width = 8, height = 5)
draw(
    p,
    heatmap_legend_side = "bottom",
    annotation_legend_side = "bottom",
    merge_legend = TRUE,
    padding = unit(c(5.5, 5.5, 5.5, 10), "points")
)
dev.off()
```

# Figure 3A - Growth Rate by Gene Class
```{r fig3a, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
df_to_plot <- timepoints %>%
  filter(growth_rate != Inf & growth_rate != -Inf) %>%
  filter(Gene_Class == "DDR" | Gene_Class == "DTA")

model_growth_rate_class <- model_growth_rate_class_fun(df_to_plot)

counts <- df_to_plot %>%
    group_by(Cohort, Gene_Class) %>%
    summarise(n = n(), .groups = "drop")

fig3a <- df_to_plot %>%
    ggplot(
        aes(
            x = Gene_Class,
            y = growth_rate,
            fill = Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    theme(
        #legend.position = "right",
        #legend.direction = "vertical",
        plot.margin = margin(2, 0, 0, 1, "cm")
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05), limit = c(NA, 1.5)) +
    do.call(geom_signif, default_sig(5, 1.75, 2, model_growth_rate_class$p.value[1], model_growth_rate_class$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(6, 1.75, 2.25, model_growth_rate_class$p.value[2], model_growth_rate_class$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(7.1, 2, 2.25, model_growth_rate_class$p.value[5], model_growth_rate_class$p.stars[5], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(5, 0.75, 1, model_growth_rate_class$p.value[3], model_growth_rate_class$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(6, 0.75, 1.25, model_growth_rate_class$p.value[4], model_growth_rate_class$p.stars[4], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(7.1, 1, 1.25, model_growth_rate_class$p.value[6], model_growth_rate_class$p.stars[6], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6))
fig3a
pdf(paste0(figures_save_path, "Figure3A_GrowthRate_GeneClass.pdf"), width = 10, height = 8)
fig3a
dev.off()
```

# Figure 3B - Growth Rate by Gene
```{r fig3b, message = FALSE, warning = FALSE, fig.width=15, fig.height=8}
df_to_plot <- timepoints %>% 
    filter(Gene_Class == "DDR") %>%
    filter(growth_rate != "Inf" & growth_rate != "-Inf")

model_growth_rate_gene <- purrr::cross_df(list(
    gene = c("TP53", "PPM1D", "CHEK2"),
    comparison = c("all", "no_untreated")
)) %>%
    pmap_dfr(function(gene, comparison) {
        print(paste(gene, comparison))
        if (comparison == "all") {
            df_subset <- df_to_plot %>% filter(Gene == gene)
            model <- glm(
                formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                data = df_subset
            ) 
        } else if (comparison == "no_untreated") {
            df_subset <- df_to_plot %>% filter(Gene == gene & Cohort != "Healthy")
            model <- glm(
                formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                data = df_subset
            )
        }
        model %>% 
            sjPlot::get_model_data(type = "est") %>%
            filter(grepl("Cohort", term)) %>%
            mutate(
                term = case_when(
                        term == "CohortCarboplatin" ~ "UntreatedVSCarboplatin",
                        term == "CohortPARPi" ~ ifelse(comparison == "all", "UntreatedVSPARPi", "CarboplatinVSPARPi"),
                        TRUE ~ term
                    ),
                gene = gene, 
                comparison = comparison
            )
    })



counts <- df_to_plot %>%
    group_by(Cohort, Gene) %>%
    summarise(n = n(), .groups = "drop")

fig3b <- df_to_plot %>%
    ggplot(
        aes(
            x = Gene,
            y = growth_rate,
            fill = Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    theme(
        #legend.position = "right",
        #legend.direction = "vertical",
        plot.margin = margin(2, 0, 0, 1, "cm")
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05), limit = c(NA, 1.5)) +
    do.call(geom_signif, default_sig(5, 0.75, 1, model_growth_rate_gene$p.value[1], model_growth_rate_gene$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(6, 0.75, 1.25, model_growth_rate_gene$p.value[2], model_growth_rate_gene$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(7.1, 1, 1.25, model_growth_rate_gene$p.value[7], model_growth_rate_gene$p.stars[7], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(5, 1.75, 2, model_growth_rate_gene$p.value[3], model_growth_rate_gene$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(6, 1.75, 2.25, model_growth_rate_gene$p.value[4], model_growth_rate_gene$p.stars[4], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(7.1, 2, 2.25, model_growth_rate_gene$p.value[8], model_growth_rate_gene$p.stars[8], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(5, 2.75, 3, model_growth_rate_gene$p.value[5], model_growth_rate_gene$p.stars[5], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(6, 2.75, 3.25, model_growth_rate_gene$p.value[6], model_growth_rate_gene$p.stars[6], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(7.1, 3, 3.25, model_growth_rate_gene$p.value[9], model_growth_rate_gene$p.stars[9], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6))
fig3b
pdf(paste0(figures_save_path, "Figure3B_GrowthRate_Gene.pdf"), width = 10, height = 8)
fig3b
dev.off()
```

# Figure 3C - Growth Rate by Specific PARP Inhibitor
```{r fig3c, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
df_to_plot <- timepoints %>%
    filter(Drug != "Carboplatin") %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(Gene_Class == "DDR" | Gene_Class == "DTA")

model_growth_rate_parp_glm <- purrr::cross_df(list(
    class = c("DDR", "DTA"),
    drug_set = c(
        "all",           # All drugs including No Treatment
        "parpi",         # Only PARPi drugs
        "nir_ruca_tala", # Niraparib, Rucaparib, Talazoparib
        "ruca_tala"      # Rucaparib, Talazoparib
    )
)) %>%
    pmap_dfr(function(class, drug_set) {
        if (drug_set == "all") {
            data <- df_to_plot %>%
                filter(Gene_Class == class) %>%
                mutate(Drug = factor(Drug, levels = c("No Treatment", "Olaparib", "Niraparib", "Rucaparib", "Talazoparib")))
            term_label <- "NoTreatment"
        } else if (drug_set == "parpi") {
            data <- df_to_plot %>%
                filter(Gene_Class == class, Cohort == "PARPi") %>%
                mutate(Drug = factor(Drug, levels = c("Olaparib", "Niraparib", "Rucaparib", "Talazoparib")))
            term_label <- "Olaparib"
        } else if (drug_set == "nir_ruca_tala") {
            data <- df_to_plot %>%
                filter(Gene_Class == class, Cohort == "PARPi", Drug %in% c("Niraparib", "Rucaparib", "Talazoparib")) %>%
                mutate(Drug = factor(Drug, levels = c("Niraparib", "Rucaparib", "Talazoparib")))
            term_label <- "Niraparib"
        } else if (drug_set == "ruca_tala") {
            data <- df_to_plot %>%
                filter(Gene_Class == class, Cohort == "PARPi", Drug %in% c("Rucaparib", "Talazoparib")) %>%
                mutate(Drug = factor(Drug, levels = c("Rucaparib", "Talazoparib")))
            term_label <- "Rucaparib"
        }
        glm(
            formula = growth_rate ~ Drug + AGE + SEX + RACE,
            data = data
        ) %>%
            sjPlot::get_model_data(type = "est") %>%
            filter(grepl("Drug", term)) %>%
            mutate(
                Class = class, 
                term = paste0(term_label, "VS", gsub("Drug", "", term))
            )
  })
model_growth_rate_parp_glm <- model_growth_rate_parp_glm %>% filter(Class == "DDR")

counts <- df_to_plot %>%
    filter(Drug != "Rucaparib") %>%
    filter(Gene_Class == "DDR") %>%
    group_by(Gene_Class, Drug) %>%
    summarise(n = n(), .groups = "drop")

fig3c <- df_to_plot %>%
    filter(Drug != "Rucaparib") %>%
    filter(Gene_Class == "DDR") %>%
    ggplot(
        aes(
            x = Gene_Class,
            y = growth_rate,
            fill = Drug
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Drug"
    ) +
    panel_theme_basic +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(2, 0, 0, 0, "cm")
    ) +
    scale_fill_manual(values = c("#BC3C29FF", "#20854EFF", "#7876B1FF", "#6F99ADFF", "#FFDC91FF")) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.1, -0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05, 0.1), limit = c(NA, 2)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 5, 0.72, 0.90, model_growth_rate_parp_glm$p.value[1], model_growth_rate_parp_glm$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +  # NoTreatment Vs Olaparib
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 6, 0.72, 1.1, model_growth_rate_parp_glm$p.value[2], model_growth_rate_parp_glm$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +   # NoTreatment Vs Niraparib
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 7, 0.72, 1.28, model_growth_rate_parp_glm$p.value[4], model_growth_rate_parp_glm$p.stars[4], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +  # NoTreatment Vs Talazoparib
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 5, 0.91, 1.28, model_growth_rate_parp_glm$p.value[7], model_growth_rate_parp_glm$p.stars[7], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +  # Olaparib Vs Talazoparib
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 6, 1.11, 1.28, model_growth_rate_parp_glm$p.value[9], model_growth_rate_parp_glm$p.stars[9], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) #+ # Niraparib Vs Talazoparib
fig3c
pdf(paste0(figures_save_path, "Figure3C_GrowthRate_ParpInhibitor.pdf"), width = 8, height = 8)
fig3c
dev.off()
```

# Figure 3D - Growth Rate by Prior Treatment
```{r fig3d, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
df_to_plot <- timepoints %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(Gene_Class == "DDR") %>%
    filter(Cohort != "Healthy")

model_growth_rate_prior_treatment <- rbind(
    glm(
        formula = growth_rate ~ NoTx_Cohort + AGE + SEX + RACE,
        data = df_to_plot %>% filter(Cohort == "Carboplatin")
    ) %>%
        sjPlot::get_model_data(type = "est") %>%
        mutate(Cohort = "Carboplatin"),
    glm(
        formula = growth_rate ~ NoTx_Cohort + AGE + SEX + RACE,
        data = df_to_plot %>% filter(Cohort == "PARPi")
    ) %>%
        sjPlot::get_model_data(type = "est") %>%
        mutate(Cohort = "PARPi")
)
model_growth_rate_prior_treatment <- model_growth_rate_prior_treatment %>% filter(grepl("NoTx_CohortPrior Treatment", term))

counts <- df_to_plot %>%
    group_by(Gene_Class, Cohort, NoTx_Cohort) %>%
    summarise(n = n(), .groups = "drop")

fig3d <- df_to_plot %>%
    ggplot(
        aes(
            x = Gene_Class,
            y = growth_rate,
            fill = NoTx_Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = c("#0072B5FF", "#4C9CCBFF", "#E18727FF", "#EAAB67FF")) +
    facet_wrap(~Cohort) +
    theme(
        legend.position = "top",
        legend.direction = "vertical",
        plot.margin = margin(2, 0, 0, 0, "cm"),
        axis.text.x = element_blank()
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05, 0.1), limits = c(NA, 0.15)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Cohort == "Carboplatin", Gene_Class == "DDR" ), 4.5, 0.8, 1.2, model_growth_rate_prior_treatment$p.value[1], model_growth_rate_prior_treatment$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Cohort == "PARPi", Gene_Class == "DDR" ), 4.5, 0.8, 1.2, model_growth_rate_prior_treatment$p.value[2], model_growth_rate_prior_treatment$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5))
fig3d
pdf(paste0(figures_save_path, "Figure3D_GrowthRate_PriorTreatment.pdf"), width = 8, height = 8)
fig3d
dev.off()
```

# Figure 4C - Treatment Expands TP53 Mutant Cells
```{r fig4c, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
fig4c <- make_mouse_cell_plot(
    mouse_data[["Figure 4C"]] %>%
        mutate(Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib", "Olaparib"))),
    cell_col = "CD45.2_Cells",
    title = "", y_lab = expression(atop("%Trp53"^"R172H/+"~"Cells", "(Normalized to 0-week)"))
)

# Check the statistics
fig4c_df <- mouse_data[["Figure 4C"]] %>%
    mutate(Mouse_Cohort = paste0(Mouse, " - ", Cohort))

anova_model <- map_dfr(combn(unique(fig4c_df$Cohort), 2, simplify = FALSE), function(pair) {
    print(pair)
    aov_ez(
        "Mouse_Cohort",
        "CD45.2_Cells",
        fig4c_df %>% filter(Cohort == pair[1] | Cohort == pair[2]),
        within = c("Week"),
        between = c("Cohort")
    ) %>%
    emmeans(., ~ Cohort) %>% 
    pairs() %>% 
    summary() %>%
    mutate(
        p.stars = case_when(
            p.value < 0.001 ~ "***",
            p.value < 0.01 ~ "**",
            p.value < 0.05 ~ "*",
            TRUE ~ ""
        )
    )
})
anova_model

fig4c <- add_significance_annotation(fig4c, format(anova_model$p.value[2], digits = 2), 13.5, 1.89, 1.12, size_text = 4)
fig4c <- add_significance_annotation(fig4c, format(anova_model$p.value[1], digits = 2), 14, 1.3, 1.12, size_text = 4)

fig4c
pdf(paste0(figures_save_path, "Figure4C_PercentageTrp53Cells.pdf"), width = 10, height = 6)
fig4c
dev.off()
```

# Figure 4D - Treatment Expands TP53 Mutant Cells
```{r fig4d, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
fig4d_to_plot <- mouse_data[["Figure 4D"]] %>%
    pivot_longer(
        cols = c("TotalBM", "LSK", "LT_HSC"),
        names_to = "Cell_Type",
        values_to = "CD45.2_Cells"
    ) %>%
    mutate(
        Cell_Type = case_when(
            Cell_Type == "LT_HSC" ~ "LT-HSC",
            Cell_Type == "TotalBM" ~ "Total BM",
            TRUE ~ Cell_Type
        ),
        Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib", "Olaparib")),
        Cell_Type = factor(Cell_Type, levels = c("Total BM", "LSK", "LT-HSC"))
    )
fig4d <- fig4d_to_plot %>%
    ggplot(
        aes(
            x = Cell_Type,
            y = CD45.2_Cells,
            fill = Cohort,
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    labs(
        x = "Bone Marrow Chimerism",
        y = expression("%"~Trp53^"R172H/+"~Cells),
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(2, 0, 0, 1, "cm")
    ) +
    scale_y_continuous(limit = c(0, 110), breaks = c(0, 25, 50, 75, 100)) +
    geom_signif(data = fig4d_to_plot, y_position = 100, xmin = 0.7, xmax = 0.9, annotations = "P<0.0001", tip_length = 0.05, textsize = 6) +
    geom_signif(data = fig4d_to_plot, y_position = 100, xmin = 1.7, xmax = 1.9, annotations = "P<0.0001", tip_length = 0.05, textsize = 6) +
    geom_signif(data = fig4d_to_plot, y_position = 95, xmin = 2.7, xmax = 2.9, annotations = "P=0.009", tip_length = 0.05, textsize = 6) +
    geom_signif(data = fig4d_to_plot, y_position = 105, xmin = 2.7, xmax = 3.1, annotations = "P=0.0427", tip_length = 0.05, textsize = 6)
fig4d
pdf(paste0(figures_save_path, "Figure4D_BoneMarrowChimerism.pdf"), width = 10, height = 6)
fig4d
dev.off()
```

# Figure 5A and 5B - Statistics - Growth Rate by Gene Class w/ Germline
```{r fig5ab_statistics, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
df_to_plot <- timepoints %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(Gene_Class == "DDR" | Gene_Class == "DTA") %>%
    filter(HRD == "No Germline" | HRD == "HRD Germline")

model_growth_rate_germline_HRD_class_glm <- purrr::cross_df(list(
    class = c("DDR", "DTA"),
    germline = c("No Germline", "HRD Germline")
)) %>%
    pmap_dfr(function(class, germline) {
        print(paste("Processing", class, germline))
        main <- if (germline == "HRD Germline" & class == "DDR") {
            glm(
                formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                data = df_to_plot %>%
                    filter(Gene_Class == class, HRD == germline) %>%
                    filter(Cohort != "Healthy") %>%
                    mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi")))
            ) %>%
                sjPlot::get_model_data(type = "est") %>%
                filter(grepl("Cohort", term)) %>%
                mutate(
                    Class = class, 
                    HRD = germline,
                    term = "CarboplatinVSPARPi"
                )
        } else {
            bind_rows(
                glm(
                    formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                    data = df_to_plot %>%
                        filter(Gene_Class == class, HRD == germline)
                ) %>%
                    sjPlot::get_model_data(type = "est") %>%
                    filter(grepl("Cohort", term)) %>%
                    mutate(
                        Class = class, 
                        HRD = germline,
                        term = case_when(
                            term == "CohortCarboplatin" ~ "NoTreatmentVSCarboplatin",
                            term == "CohortPARPi" ~ "NoTreatmentVSPARPi"
                        )
                    ),
                glm(
                    formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                    data = df_to_plot %>%
                        filter(Gene_Class == class, HRD == germline) %>%
                        filter(Cohort != "Healthy") %>%
                        mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi")))
                ) %>%
                    sjPlot::get_model_data(type = "est") %>%
                    filter(grepl("Cohort", term)) %>%
                    mutate(
                        Class = class, 
                        HRD = germline,
                        term = "CarboplatinVSPARPi"
                    )
            )
        }
    })
# Add the HRD effect for each class and cohort
hrd_effect <- purrr::cross_df(list(
    class = c("DDR", "DTA"),
    cohort = c("Carboplatin", "PARPi")
)) %>%
    pmap_dfr(function(class, cohort) {
        print(paste("Processing", class, cohort))
        glm(
            formula = growth_rate ~ HRD + AGE + SEX + RACE,
            data = df_to_plot %>%
                filter(Gene_Class == class) %>%
                filter(Cohort == cohort) %>%
                mutate(HRD = factor(HRD, levels = c("No Germline", "HRD Germline")))
        ) %>%
            sjPlot::get_model_data(type = "est") %>%
            filter(term == "HRDHRD Germline") %>%
            mutate(
                term = "HRDNoGermline",
                Class = class,
                HRD = cohort
            )
    })
model_growth_rate_germline_HRD_class_glm <- bind_rows(model_growth_rate_germline_HRD_class_glm, hrd_effect %>% filter(Class == "DDR"))
model_growth_rate_germline_HRD_dta_glm <- model_growth_rate_germline_HRD_class_glm %>% filter(Class == "DTA")
model_growth_rate_germline_HRD_dta_glm <- bind_rows(model_growth_rate_germline_HRD_dta_glm, hrd_effect %>% filter(Class == "DTA"))

model_growth_rate_germline_HRD_class_glm <- model_growth_rate_germline_HRD_class_glm %>% filter(Class == "DDR")

counts <- df_to_plot %>%
    group_by(Cohort, Gene_Class, HRD) %>%
    summarise(n = n(), .groups = "drop")
```

# Figure 5A - Growth Rate by Gene Class w/ Germline
```{r fig5a, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
fig5a <- df_to_plot %>%
    filter(Gene_Class == "DDR") %>%
    ggplot(
        aes(
            x = HRD,
            y = growth_rate,
            fill = Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts %>% filter(Gene_Class == "DDR"), aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "DDR",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    theme(
        legend.text = element_text(size = 20),
        plot.margin = margin(0, 0, 0, 1, "cm")
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), limit = c(NA, 1.5), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 5, 0.75, 1, model_growth_rate_germline_HRD_class_glm$p.value[1], model_growth_rate_germline_HRD_class_glm$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 6, 0.75, 1.25, model_growth_rate_germline_HRD_class_glm$p.value[2], model_growth_rate_germline_HRD_class_glm$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 7, 1, 1.25, model_growth_rate_germline_HRD_class_glm$p.value[3], model_growth_rate_germline_HRD_class_glm$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 4.5, 1, 1.80, model_growth_rate_germline_HRD_class_glm$p.value[5], model_growth_rate_germline_HRD_class_glm$p.stars[5], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 5.5, 1.25, 2.20, model_growth_rate_germline_HRD_class_glm$p.value[6], model_growth_rate_germline_HRD_class_glm$p.stars[6], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 6.5, 1.80, 2.20, model_growth_rate_germline_HRD_class_glm$p.value[4], model_growth_rate_germline_HRD_class_glm$p.stars[4], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6))
fig5a
pdf(paste0(figures_save_path, "Figure5A_GrowthRate_Germline_DDR.pdf"), width = 8, height = 8)
fig5a
dev.off()
```

# Figure 5B - DTA Growth Rate by Gene Class w/ Germline
```{r fig5b, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
fig5b <- df_to_plot %>%
    filter(Gene_Class == "DTA") %>%
    ggplot(
        aes(
            x = HRD,
            y = growth_rate,
            fill = Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts %>% filter(Gene_Class == "DTA"), aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "DTA",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    theme(
        legend.text = element_text(size = 20),
        plot.margin = margin(0, 0, 0, 1, "cm")
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), limit = c(NA, 1.5), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05))
    # do.call(geom_signif, default_sig_data(df_to_plot, 5, 0.75, 1, model_growth_rate_germline_HRD_dta_glm$p.value[1], model_growth_rate_germline_HRD_dta_glm$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5)) +
    # do.call(geom_signif, default_sig_data(df_to_plot, 6, 0.75, 1.25, model_growth_rate_germline_HRD_dta_glm$p.value[2], model_growth_rate_germline_HRD_dta_glm$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5)) +
    # do.call(geom_signif, default_sig_data(df_to_plot, 7, 1, 1.25, model_growth_rate_germline_HRD_dta_glm$p.value[3], model_growth_rate_germline_HRD_dta_glm$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5)) +

    # do.call(geom_signif, default_sig_data(df_to_plot, 5, 1.75, 2, model_growth_rate_germline_HRD_dta_glm$p.value[4], model_growth_rate_germline_HRD_dta_glm$p.stars[4], show_values = TRUE, hide_ns = TRUE, size = 0.5)) +
    # do.call(geom_signif, default_sig_data(df_to_plot, 6, 1.75, 2.25, model_growth_rate_germline_HRD_dta_glm$p.value[5], model_growth_rate_germline_HRD_dta_glm$p.stars[5], show_values = TRUE, hide_ns = TRUE, size = 0.5)) +
    # do.call(geom_signif, default_sig_data(df_to_plot, 7, 2, 2.25, model_growth_rate_germline_HRD_dta_glm$p.value[6], model_growth_rate_germline_HRD_dta_glm$p.stars[6], show_values = TRUE, hide_ns = TRUE, size = 0.5)) +

    # do.call(geom_signif, default_sig_data(df_to_plot, 2.5, 1, 2, model_growth_rate_germline_HRD_dta_glm$p.value[7], model_growth_rate_germline_HRD_dta_glm$p.stars[7], show_values = TRUE, hide_ns = TRUE, size = 0.5)) +
    # do.call(geom_signif, default_sig_data(df_to_plot, 3, 1.25, 2.25, model_growth_rate_germline_HRD_dta_glm$p.value[8], model_growth_rate_germline_HRD_dta_glm$p.stars[8], show_values = TRUE, hide_ns = TRUE, size = 0.5))
fig5b
pdf(paste0(figures_save_path, "Figure5B_GrowthRate_Germline_DTA.pdf"), width = 8, height = 8)
fig5b
dev.off()
```

# Figure 5C - Growth Rate by Gene w/ Germline
```{r fig5c, message = FALSE, warning = FALSE, fig.width=15, fig.height=8}
df_to_plot <- timepoints %>% 
    filter(Gene_Class == "DDR") %>%
    filter(growth_rate != "Inf" & growth_rate != "-Inf") %>%
    filter(HRD == "No Germline" | HRD == "HRD Germline")

model_growth_rate_germline_gene_glm <- purrr::cross_df(list(
    gene = c("TP53", "PPM1D", "CHEK2"),
    germline = c("No Germline", "HRD Germline")
)) %>%
    pmap_dfr(function(gene, germline) {
        print(paste("Processing", gene, germline))
        main <- if (germline == "HRD Germline") {
            glm(
                formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                data = df_to_plot %>%
                    filter(Gene == gene, HRD == germline) %>%
                    filter(Cohort != "Healthy") %>%
                    mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi")))
            ) %>%
                sjPlot::get_model_data(type = "est") %>%
                filter(grepl("Cohort", term)) %>%
                mutate(
                    Gene = gene, 
                    HRD = germline,
                    term = "CarboplatinVSPARPi"
                )
        } else {
            bind_rows(
                glm(
                    formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                    data = df_to_plot %>% 
                        filter(Gene == gene, HRD == germline)
                ) %>%
                    sjPlot::get_model_data(type = "est") %>%
                    filter(grepl("Cohort", term)) %>%
                    mutate(
                        Gene = gene, 
                        HRD = germline,
                        term = case_when(
                            term == "CohortCarboplatin" ~ "NoTreatmentVSCarboplatin",
                            term == "CohortPARPi" ~ "NoTreatmentVSPARPi"
                        )
                    ),
                glm(
                    formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                    data = df_to_plot %>%
                        filter(Gene == gene, HRD == germline) %>%
                        filter(Cohort != "Healthy") %>%
                        mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi")))
                ) %>%
                    sjPlot::get_model_data(type = "est") %>%
                    filter(grepl("Cohort", term)) %>%
                    mutate(
                        Gene = gene, 
                        HRD = germline,
                        term = "CarboplatinVSPARPi"
                    ),
                # Add the HRD effect for each gene and cohort
                map_dfr(c("Carboplatin", "PARPi"), function(cohort) {
                    glm(
                        formula = growth_rate ~ HRD + AGE + SEX + RACE,
                        data = df_to_plot %>%
                            filter(Gene == gene, Cohort == cohort) %>%
                            mutate(HRD = factor(HRD, levels = c("No Germline", "HRD Germline")))
                    ) %>%
                        sjPlot::get_model_data(type = "est") %>%
                        filter(term == "HRDHRD Germline") %>%
                        mutate(
                            term = "HRDNoGermline",
                            Gene = gene,
                            HRD = cohort
                        )
                })
            )
        }
    })

counts <- df_to_plot %>%
    group_by(Cohort, Gene, HRD) %>%
    summarise(n = n(), .groups = "drop")

fig5c <- df_to_plot %>%
    filter(Gene %in% c("PPM1D", "TP53", "CHEK2")) %>%
    ggplot(
        aes(
            x = HRD,
            y = growth_rate,
            fill = Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    facet_wrap(~Gene) +
    theme(
        axis.text.x = element_text(size = 22),
        legend.text = element_text(size = 20),
        plot.margin = margin(0, 0, 0, 1, "cm")
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05), limit = c(NA, 1.5)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "TP53"), 5, 0.75, 1, model_growth_rate_germline_gene_glm$p.value[1], model_growth_rate_germline_gene_glm$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "TP53"), 6, 0.75, 1.25, model_growth_rate_germline_gene_glm$p.value[2], model_growth_rate_germline_gene_glm$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "TP53"), 7, 1, 1.25, model_growth_rate_germline_gene_glm$p.value[3], model_growth_rate_germline_gene_glm$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "TP53"), 6, 1.8, 2.2, model_growth_rate_germline_gene_glm$p.value[16], model_growth_rate_germline_gene_glm$p.stars[16], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "TP53"), 6, 1, 1.8, model_growth_rate_germline_gene_glm$p.value[4], model_growth_rate_germline_gene_glm$p.stars[4], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "TP53"), 5, 1.25, 2.2, model_growth_rate_germline_gene_glm$p.value[5], model_growth_rate_germline_gene_glm$p.stars[5], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +

    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "PPM1D"), 5, 0.75, 0.99, model_growth_rate_germline_gene_glm$p.value[6], model_growth_rate_germline_gene_glm$p.stars[6], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "PPM1D"), 6, 0.75, 1.24, model_growth_rate_germline_gene_glm$p.value[7], model_growth_rate_germline_gene_glm$p.stars[7], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "PPM1D"), 7, 1, 1.25, model_growth_rate_germline_gene_glm$p.value[8], model_growth_rate_germline_gene_glm$p.stars[8], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "PPM1D"), 5.2, 1.8, 2.2, model_growth_rate_germline_gene_glm$p.value[17], model_growth_rate_germline_gene_glm$p.stars[17], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "PPM1D"), 5, 1, 1.8, model_growth_rate_germline_gene_glm$p.value[9], model_growth_rate_germline_gene_glm$p.stars[9], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "PPM1D"), 6, 1.26, 2.2, model_growth_rate_germline_gene_glm$p.value[10], model_growth_rate_germline_gene_glm$p.stars[10], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +

    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "CHEK2"), 5, 0.75, 1, model_growth_rate_germline_gene_glm$p.value[11], model_growth_rate_germline_gene_glm$p.stars[11], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "CHEK2"), 6, 0.75, 1.25, model_growth_rate_germline_gene_glm$p.value[12], model_growth_rate_germline_gene_glm$p.stars[12], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "CHEK2"), 7, 1, 1.25, model_growth_rate_germline_gene_glm$p.value[13], model_growth_rate_germline_gene_glm$p.stars[13], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "CHEK2"), 4, 1.8, 2.2, model_growth_rate_germline_gene_glm$p.value[18], model_growth_rate_germline_gene_glm$p.stars[18], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +      # Carboplatin to PARPi
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "CHEK2"), 5.5, 1, 1.8, model_growth_rate_germline_gene_glm$p.value[14], model_growth_rate_germline_gene_glm$p.stars[14], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +      # Carboplatin
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene == "CHEK2"), 6, 1.25, 2.2, model_growth_rate_germline_gene_glm$p.value[15], model_growth_rate_germline_gene_glm$p.stars[15], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6))       # PARPi
fig5c
pdf(paste0(figures_save_path, "Figure5C_GrowthRate_Gene_Germline.pdf"), width = 15, height = 8)
fig5c
dev.off()
```

# Figure 6B - Treatment Expands BRCA;TP53 Mutants in Peripheral Blood
```{r fig6b, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
fig6b_df <- mouse_data[["Figure 6B"]] %>%
    mutate(Mouse_Cohort = paste0(Mouse, " - ", Cohort))

anova_model_fig6b <- map_dfr(combn(unique(fig6b_df$Cohort), 2, simplify = FALSE), function(pair) {
    print(pair)
    aov_ez(
        "Mouse_Cohort",
        "CD45.2_Cells",
        fig6b_df %>% filter(Cohort == pair[1] | Cohort == pair[2]),
        within = c("Week"),
        between = c("Cohort")
    ) %>%
    emmeans(., ~ Cohort) %>% 
    pairs() %>% 
    summary() %>%
    mutate(
        p.stars = case_when(
            p.value < 0.001 ~ "***",
            p.value < 0.01 ~ "**",
            p.value < 0.05 ~ "*",
            TRUE ~ ""
        )
    )
})
anova_model_fig6b

fig6b <- make_mouse_cell_plot(
    mouse_data[["Figure 6B"]] %>%
        mutate(Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib"))),
    cell_col = "CD45.2_Cells",
    y_limits = c(0, 3.5),
    title = "", y_lab = expression(atop("%" ~ Brca1^"fl/+"*";"*Trp53^"R172H/+" ~ "Cells", "(Normalized to 0-Week)"))
)
fig6b
pdf(paste0(figures_save_path, "Figure6B_PeripheralBloodChimerism.pdf"), width = 10, height = 6)
fig6b
dev.off()
```

# Figure 6C - Treatment Expands BRCA;TP53 Mutants in Bone Marrow
```{r fig6c, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
fig6c <- mouse_data[["Figure 6C"]] %>%
    pivot_longer(
        cols = c("LSK", "LT_HSC"),
        names_to = "Cell_Type",
        values_to = "CD45.2_Cells"
    ) %>%
    mutate(
        Cell_Type = ifelse(Cell_Type == "LT_HSC", "LT-HSC", Cell_Type),
        Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib")),
        Cell_Type = factor(Cell_Type, levels = c("LSK", "LT-HSC"))
    ) %>%
    ggplot(
        aes(
            x = Cell_Type,
            y = CD45.2_Cells,
            fill = Cohort,
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    labs(
        x = "",
        y = expression("%"~Brca1^"fl/+"*";"*Trp53^"R172H/+"~Cells),
        fill = "Cohort",
        title = "Bone Marrow Chimerism"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(2, 0, 0, 1, "cm"),
        plot.title = element_text(hjust = 0.5)
    ) +
    scale_y_log10(breaks = c(1, 10, 100), labels = c(1, 10, 100), limits = c(1, 100))
fig6c
pdf(paste0(figures_save_path, "Figure6C_BoneMarrowChimerism.pdf"), width = 8, height = 8)
fig6c
dev.off()
```

# Figure 6D - Chimerism 12 weeks post-treatmentin peripheral blood
```{r fig6d, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
fig6d_to_plot <- mouse_data[["Figure 6D"]] %>%
    pivot_longer(
        cols = c("WT", "BRCA"),
        names_to = "Background",
        values_to = "CD45.2_Cells"
    ) %>%
    filter(!is.na(CD45.2_Cells)) %>%
    mutate(
        Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib")),
        Background = ifelse(Background == "BRCA", "Brca1 fl/+", Background),
        Background = factor(Background, levels = c("WT", "Brca1 fl/+"))
    )

fig6d <- fig6d_to_plot %>%
    ggplot(
        aes(
            x = Cohort,
            y = CD45.2_Cells,
            fill = Background
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    labs(
        x = "",
        y = expression(atop("%" ~ Brca1^"fl/+"*";"*Trp53^"R172H/+" ~ "Cells", "(Normalized to Vehicle)")),
        fill = "Cohort",
        title = "Leukocyte Chimerism"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(1, 1, 1, 1, "cm"),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis labels
    ) +
    geom_signif(data = fig6d_to_plot, y_position = 3.5, xmin = 0.85, xmax = 1.84, annotations = "P=0.0002", tip_length = 0.05, textsize = 6) +
    geom_signif(data = fig6d_to_plot, y_position = 3.8, xmin = 1.15, xmax = 3.15, annotations = "P=0.0236", tip_length = 0.05, textsize = 6) +
    geom_signif(data = fig6d_to_plot, y_position = 3.5, xmin = 1.86, xmax = 2.85, annotations = "P=0.0118", tip_length = 0.05, textsize = 6) +
    geom_signif(data = fig6d_to_plot, y_position = 3, xmin = 1.85, xmax = 2.15, annotations = "P<0.0001", tip_length = 0.05, textsize = 6) +
    geom_signif(data = fig6d_to_plot, y_position = 2.5, xmin = 2.85, xmax = 3.15, annotations = "P=0.0016", tip_length = 0.05, textsize = 6)
fig6d
pdf(paste0(figures_save_path, "Figure6D_LeukocyteChimerism.pdf"), width = 8, height = 8)
fig6d
dev.off()
```

# Figure 6E -  Chimerism 12 weeks post-treatmentin bone marrow
```{r fig6e, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
fig6e_to_plot <- mouse_data[["Figure 6E"]] %>%
    pivot_longer(
        cols = c("WT", "BRCA"),
        names_to = "Background",
        values_to = "CD45.2_Cells"
    ) %>%
    filter(!is.na(CD45.2_Cells)) %>%
    mutate(
        Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib")),
        Background = ifelse(Background == "BRCA", "Brca1 fl/+", Background),
        Background = factor(Background, levels = c("WT", "Brca1 fl/+"))
    )
fig6e <- fig6e_to_plot %>%
    ggplot(
        aes(
            x = Cohort,
            y = CD45.2_Cells,
            fill = Background
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    labs(
        x = "",
        y = expression(atop("%" ~ Brca1^"fl/+"*";"*Trp53^"R172H/+" ~ "Cells", "(Normalized to Vehicle)")),
        fill = "Cohort",
        title = "Bone Marrow Chimerism"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(1, 1, 1, 1, "cm"),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis labels
    ) +
    ylim(NA, 3) +
    geom_signif(data = fig6e_to_plot, y_position = 2.5, xmin = 0.85, xmax = 1.84, annotations = "P=0.0001", tip_length = 0.05, textsize = 6) +
    geom_signif(data = fig6e_to_plot, y_position = 2.8, xmin = 1.85, xmax = 2.15, annotations = "P=0.0003", tip_length = 0.05, textsize = 6)
fig6e
pdf(paste0(figures_save_path, "Figure6E_BoneMarrowChimerism.pdf"), width = 8, height = 8)
fig6e
dev.off()
```

# Figure 7 - BRCA Het increases DNA Damage along with TP53 Mutations
```{r fig7, message = FALSE, warning = FALSE, fig.width=17, fig.height=10}
fig7b <- mouse_data[["Figure 7B"]] %>%
    pivot_longer(cols = c("Cre_Ctrl", "Cre_+Tal", "R172H_Het_Ctrl", "R172H_Het_+Tal", "BRCA_Het_Ctrl", "BRCA_Het_+Tal", "Double_Ctrl", "Double_+Tal"), names_to = "Cohort", values_to = "Data") %>%
    mutate(Cohort = factor(Cohort, levels = c("Cre_Ctrl", "Cre_+Tal", "R172H_Het_Ctrl", "R172H_Het_+Tal", "BRCA_Het_Ctrl", "BRCA_Het_+Tal", "Double_Ctrl", "Double_+Tal"))) %>%
    mutate(
        Background = case_when(
            Cohort %in% c("Cre_Ctrl", "Cre_+Tal") ~ "Cre+/-",
            Cohort %in% c("R172H_Het_Ctrl", "R172H_Het_+Tal") ~ "Trp53R172H/+",
            Cohort %in% c("BRCA_Het_Ctrl", "BRCA_Het_+Tal") ~ "Brca1fl/+",
            Cohort %in% c("Double_Ctrl", "Double_+Tal") ~ "Trp53R172H/+; Brca1fl/+"
        ),
        Background = factor(
            Background,
            levels = c(
                "Cre+/-",
                "Trp53R172H/+",
                "Brca1fl/+",
                "Trp53R172H/+; Brca1fl/+"
            )
        )
    ) %>%
    ggplot(
        aes(
            x = Cohort,
            y = Data,
            fill = Background
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    labs(
        x = "",
        y = "Olive Moment",
        fill = "Mutation",
        title = "Comet Assay - DNA Double Strand Breaks"
    ) +
    panel_theme_basic +
    scale_fill_nejm(
        labels = c(
            expression(Cre^{"+/-"}),
            expression(Trp53^{R172H/"+"}),
            expression(Brca1^{fl/"+"}),
            expression(Trp53^{R172H/"+"} * ";" ~ Brca1^{fl/"+"})
        )
    ) +
    scale_x_discrete(
        labels = c(
            Cre_Ctrl = "Control",
            `Cre_+Tal` = "Talazoparib",
            R172H_Het_Ctrl = "Control",
            `R172H_Het_+Tal` = "Talazoparib",
            BRCA_Het_Ctrl = "Control",
            `BRCA_Het_+Tal` = "Talazoparib",
            Double_Ctrl = "Control",
            `Double_+Tal` = "Talazoparib"
        )
    ) +
    theme(
        legend.position = "top",
        legend.direction = "horizontal",
        plot.margin = margin(1, 1, 1, 1, "cm"),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis labels
    ) +
    # Main Groups
    geom_signif(y_position = 75, xmin = 1, xmax = 2, annotations = "P=0.0005", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 75, xmin = 3, xmax = 4, annotations = "P=0.0015", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 75, xmin = 5, xmax = 6, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 75, xmin = 7, xmax = 8, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    # Cre to Trp Tal
    geom_signif(y_position = 85, xmin = 2, xmax = 4, annotations = "P=0.0364", tip_length = 0.02, textsize = 5) +
    # Trp to Brca Tal
    geom_signif(y_position = 85, xmin = 4, xmax = 6, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    # Crep to Brca Tal
    geom_signif(y_position = 95, xmin = 2, xmax = 6, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    # Cre to Double Tal
    geom_signif(y_position = 105, xmin = 2, xmax = 8, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    # Trp to Double Tal
    geom_signif(y_position = 115, xmin = 4, xmax = 8, annotations = "P=0.0053", tip_length = 0.02, textsize = 5)
fig7b
pdf(paste0(figures_save_path, "Figure7B_CometAssay.pdf"), width = 10, height = 8)
fig7b
dev.off()

fig7c <- mouse_data[["Figure 7C"]] %>%
    pivot_longer(cols = c("Cre_Ctrl", "Cre_+Tal", "R172H_Het_Ctrl", "R172H_Het_+Tal", "BRCA_Het_Ctrl", "BRCA_Het_+Tal", "Double_Ctrl", "Double_+Tal"), names_to = "Cohort", values_to = "Data") %>%
    mutate(Cohort = factor(Cohort, levels = c("Cre_Ctrl", "Cre_+Tal", "R172H_Het_Ctrl", "R172H_Het_+Tal", "BRCA_Het_Ctrl", "BRCA_Het_+Tal", "Double_Ctrl", "Double_+Tal"))) %>%
    mutate(
        Background = case_when(
            Cohort %in% c("Cre_Ctrl", "Cre_+Tal") ~ "Cre+/-",
            Cohort %in% c("R172H_Het_Ctrl", "R172H_Het_+Tal") ~ "Trp53R172H/+",
            Cohort %in% c("BRCA_Het_Ctrl", "BRCA_Het_+Tal") ~ "Brca1fl/+",
            Cohort %in% c("Double_Ctrl", "Double_+Tal") ~ "Trp53R172H/+; Brca1fl/+"
        ),
        Background = factor(
            Background,
            levels = c(
                "Cre+/-",
                "Trp53R172H/+",
                "Brca1fl/+",
                "Trp53R172H/+; Brca1fl/+"
            )
        )
    ) %>%
    ggplot(
        aes(
            x = Cohort,
            y = Data,
            fill = Background
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    labs(
        x = "",
        y = "% Cells with >10 foci",
        fill = "Mutation",
        title = "gH2AX+ Cells"
    ) +
    panel_theme_basic +
    scale_fill_nejm(
        labels = c(
            expression(Cre^{"+/-"}),
            expression(Trp53^{R172H/"+"}),
            expression(Brca1^{fl/"+"}),
            expression(Trp53^{R172H/"+"} * ";" ~ Brca1^{fl/"+"})
        )
    ) +
    scale_x_discrete(
        labels = c(
            Cre_Ctrl = "Control",
            `Cre_+Tal` = "Talazoparib",
            R172H_Het_Ctrl = "Control",
            `R172H_Het_+Tal` = "Talazoparib",
            BRCA_Het_Ctrl = "Control",
            `BRCA_Het_+Tal` = "Talazoparib",
            Double_Ctrl = "Control",
            `Double_+Tal` = "Talazoparib"
        )
    ) +
    theme(
        legend.position = "top",
        legend.direction = "horizontal",
        plot.margin = margin(1, 1, 1, 1, "cm"),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis labels
    ) +
    # Main Groups
    scale_y_continuous(limits = c(0, 140), breaks = seq(0, 100, by = 25)) +
    geom_signif(y_position = 105, xmin = 1, xmax = 2, annotations = "P=0.6769", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 105, xmin = 3, xmax = 4, annotations = "P=0.0486", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 105, xmin = 5, xmax = 6, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 105, xmin = 7, xmax = 8, annotations = "P=0.0469", tip_length = 0.02, textsize = 5) +
    # Trp to Brca Ctrl
    geom_signif(y_position = 115, xmin = 4, xmax = 6, annotations = "P=0.0013", tip_length = 0.02, textsize = 5) +
    # Cre to Brca Tal
    geom_signif(y_position = 125, xmin = 2, xmax = 6, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    # Cre to Double Het Tal
    geom_signif(y_position = 135, xmin = 2, xmax = 8, annotations = "P=0.0053", tip_length = 0.02, textsize = 5)
fig7c
pdf(paste0(figures_save_path, "Figure7C_gH2AX.pdf"), width = 10, height = 8)
fig7c
dev.off()

fig7d <- mouse_data[["Figure 7D"]] %>%
    pivot_longer(cols = c("Cre_Ctrl", "Cre_+Tal", "R172H_Het_Ctrl", "R172H_Het_+Tal", "BRCA_Het_Ctrl", "BRCA_Het_+Tal", "Double_Ctrl", "Double_+Tal"), names_to = "Cohort", values_to = "Data") %>%
    mutate(Cohort = factor(Cohort, levels = c("Cre_Ctrl", "Cre_+Tal", "R172H_Het_Ctrl", "R172H_Het_+Tal", "BRCA_Het_Ctrl", "BRCA_Het_+Tal", "Double_Ctrl", "Double_+Tal"))) %>%
    mutate(
        Background = case_when(
            Cohort %in% c("Cre_Ctrl", "Cre_+Tal") ~ "Cre+/-",
            Cohort %in% c("R172H_Het_Ctrl", "R172H_Het_+Tal") ~ "Trp53R172H/+",
            Cohort %in% c("BRCA_Het_Ctrl", "BRCA_Het_+Tal") ~ "Brca1fl/+",
            Cohort %in% c("Double_Ctrl", "Double_+Tal") ~ "Trp53R172H/+; Brca1fl/+"
        ),
        Background = factor(
            Background,
            levels = c(
                "Cre+/-",
                "Trp53R172H/+",
                "Brca1fl/+",
                "Trp53R172H/+; Brca1fl/+"
            )
        ),
        Treatment = case_when(
            Cohort %in% c("Cre_Ctrl", "R172H_Het_Ctrl", "BRCA_Het_Ctrl", "Double_Ctrl") ~ "Ctrl",
            Cohort %in% c("Cre_+Tal", "R172H_Het_+Tal", "BRCA_Het_+Tal", "Double_+Tal") ~ "+Tal"
        )
    ) %>%
    ggplot(
        aes(
            x = Cohort,
            y = Data,
            fill = Background
        )
    ) +
    geom_bar(aes(group = Cohort), stat = "summary", fun = "mean", position = position_dodge(width = 0.8), width = 0.7, color = "black") +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_errorbar(aes(group = Cohort),stat = "summary", fun.data = "mean_se", position = position_dodge(width = 0.8), width = 0.4) +
    labs(
        x = "",
        y = "% Cleaved Caspase3+ Cells",
        fill = "Mutation",
        title = "Cleaved Caspase3+"
    ) +
    panel_theme_basic +
    scale_fill_nejm(
        labels = c(
            expression(Cre^{"+/-"}),
            expression(Trp53^{R172H/"+"}),
            expression(Brca1^{fl/"+"}),
            expression(Trp53^{R172H/"+"} * ";" ~ Brca1^{fl/"+"})
        )
    ) +
    scale_x_discrete(
        labels = c(
            Cre_Ctrl = "Control",
            `Cre_+Tal` = "Talazoparib",
            R172H_Het_Ctrl = "Control",
            `R172H_Het_+Tal` = "Talazoparib",
            BRCA_Het_Ctrl = "Control",
            `BRCA_Het_+Tal` = "Talazoparib",
            Double_Ctrl = "Control",
            `Double_+Tal` = "Talazoparib"
        )
    ) +
    theme(
        legend.position = "top",
        legend.direction = "horizontal",
        plot.margin = margin(1, 1, 1, 1, "cm"),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1) # Rotate x-axis labels
    ) +
    # Main Groups
    scale_y_continuous(limits = c(0, 130), breaks = seq(0, 100, by = 25), expand = expansion(mult = c(0, 0.05))) +
    geom_signif(y_position = 85, xmin = 1, xmax = 2, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 85, xmin = 3, xmax = 4, annotations = "P=0.0085", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 85, xmin = 5, xmax = 6, annotations = "P<0.0001", tip_length = 0.02, textsize = 5) +
    geom_signif(y_position = 85, xmin = 7, xmax = 8, annotations = "P=0.0007", tip_length = 0.02, textsize = 5) +
    # Brca to Double Het Ctrl
    geom_signif(y_position = 95, xmin = 5, xmax = 7, annotations = "P=0.0006", tip_length = 0.02, textsize = 5) +
    # Cre to Double Het Ctrl
    geom_signif(y_position = 105, xmin = 1, xmax = 7, annotations = "P=0.0277", tip_length = 0.02, textsize = 5) +
    # Brca to Double Het Tal
    geom_signif(y_position = 115, xmin = 6, xmax = 8, annotations = "P=0.0305", tip_length = 0.02, textsize = 5) +
    # Trp to Double Het Tal
    geom_signif(y_position = 125, xmin = 4, xmax = 8, annotations = "P=0.0177", tip_length = 0.02, textsize = 5)
fig7d
pdf(paste0(figures_save_path, "Figure7D_CleavedCaspase3.pdf"), width = 10, height = 8)
fig7d
dev.off()
```

# Extended Data Figure 1 - Spider Plots by VAF
```{r extdata_fig1, message = FALSE, warning = FALSE, fig.width=17, fig.height=10}
avg_change_a <- timepoints %>% filter(VAF_Category == "<=2%") %>% filter(!is.na(change_in_VAF_months), change_in_months < 75, Gene_Class == 'DDR'| Gene_Class == 'DTA') %>% group_by(Gene_Class, Cohort) %>% summarise(n = mean(change_in_VAF))
avg_change_b <- timepoints %>% filter(VAF_Category == ">2%") %>% filter(!is.na(change_in_VAF_months), change_in_months < 75, Gene_Class == 'DDR'| Gene_Class == 'DTA') %>% group_by(Gene_Class, Cohort) %>% summarise(n = mean(change_in_VAF))

timepoints %>%
    filter(VAF_Category == ">2%") %>%
    group_by(Cohort) %>%
    summarise(
        mean_change_in_VAF = median(change_in_VAF),
        mean_change_in_VAF_per_month = median(change_in_VAF_months)
    )

extdata_fig1_a <- timepoints %>%
    filter(VAF_Category == "<=2%") %>%
    filter(!is.na(change_in_VAF_months), change_in_months < 75, Gene_Class == 'DDR'| Gene_Class == 'DTA') %>%
    ggplot(
        aes(
            x = change_in_months,
            y = change_in_VAF,
            fill = Cohort,
            color = Cohort
        )
    ) +
    geom_segment(aes(xend = 0, yend = 0), size = 0.1) +
    geom_point() +
    labs(
        x = "",
        y = "Change in VAF",
        fill = "Cohort",
        title = "VAF <=2%"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    scale_color_manual(values = treatment_colors) +
    scale_y_continuous(
        trans = scales::pseudo_log_trans(0.001),
        limits = \(x) {
            c(-max(abs(x)), max(abs(x)))
        }
    ) +
    facet_wrap(Gene_Class~Cohort, ncol = 3, nrow = 2) +
    theme(
        strip.text = element_blank(),
        plot.title = element_text(hjust = 0, vjust = 2, size = 20),
        plot.margin = margin(1, 1, -1, 1, "cm"),
        panel.spacing = unit(2, "lines"),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16)
    )

extdata_fig1_b <- timepoints %>%
    filter(VAF_Category == ">2%") %>%
    filter(!is.na(change_in_VAF_months), change_in_months < 75, Gene_Class == 'DDR'| Gene_Class == 'DTA') %>%
    ggplot(
        aes(
            x = change_in_months,
            y = change_in_VAF,
            fill = Cohort,
            color = Cohort
        )
    ) +
    geom_segment(aes(xend = 0, yend = 0), size = 0.1) +
    geom_point() +
    labs(
        x = "",
        y = "",
        fill = "Cohort",
        title = "VAF >2%"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    scale_color_manual(values = treatment_colors) +
    scale_y_continuous(
        trans = scales::pseudo_log_trans(0.001),
        limits = \(x) {
            c(-max(abs(x)), max(abs(x)))
        }
    ) +
    facet_wrap(Gene_Class~Cohort, ncol = 3, nrow = 2) +
    theme(
        strip.text = element_blank(),
        plot.title = element_text(hjust = 0, vjust = 2, size = 20),
        plot.margin = margin(1, 1, -1, 1, "cm"),
        panel.spacing = unit(2, "lines"),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16)
    )

legend <- ggpubr::get_legend(extdata_fig1_a)
extdata_fig1_a <- extdata_fig1_a + theme(legend.position = "none")
extdata_fig1_b <- extdata_fig1_b + theme(legend.position = "none")

extdata_fig1 <- plot_grid(
    plot_grid(extdata_fig1_a, extdata_fig1_b, labels = c("a", "b"), label_size = 30),
    ggdraw() + draw_label("Months", size = 20),
    legend,
    ncol = 1, nrow = 3,
    rel_widths = c(2, 1, 1),
    rel_heights = c(10, 0.5, 1)
) +
    draw_label("DDR", x = 0.25, y = 0.97, size = 20) +
    draw_label("DTA", x = 0.25, y = 0.5, size = 20) +
    draw_label("DDR", x = 0.75, y = 0.97, size = 20) +
    draw_label("DTA", x = 0.75, y = 0.5, size = 20)
extdata_fig1
pdf(paste0(figures_save_path, "ExtFigure1_SpiderPlots_VAF.pdf"), width = 17, height = 10)
extdata_fig1
dev.off()
```

# Extended Data Figure 2 - Growth Rates for VAF Category
```{r extdata_fig2_growth_vaf, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
df_to_plot <- timepoints %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(Gene_Class == "DDR" | Gene_Class == "DTA")

#Statistics
model_growth_rate_class_lessthan2 <- model_growth_rate_class_fun(df_to_plot %>% filter(VAF_Category == "<=2%"))
model_growth_rate_class_greaterthan2 <- model_growth_rate_class_fun(df_to_plot %>% filter(VAF_Category == ">2%"))

counts <- df_to_plot %>%
    group_by(Cohort, Gene_Class, VAF_Category) %>%
    summarise(n = n(), .groups = "drop")

extdata_fig2 <- df_to_plot %>%
    ggplot(
        aes(
            x = Cohort,
            y = growth_rate,
            fill = Cohort,
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort",
        title = "Growth Rate by VAF Category"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    scale_color_manual(values = treatment_colors) +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(0, 0, 0, 1, "cm"),
        plot.title = element_text(hjust = 0.5, size = 20),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16)
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05), limits = c(NA, 8)) +
    facet_wrap(Gene_Class ~ VAF_Category) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(VAF_Category == "<=2%") %>% filter(Gene_Class == "DDR"), 6, 1, 2, model_growth_rate_class_lessthan2$p.value[3], model_growth_rate_class_lessthan2$p.stars[3], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(VAF_Category == "<=2%") %>% filter(Gene_Class == "DDR"), 6.5, 1, 3, model_growth_rate_class_lessthan2$p.value[4], model_growth_rate_class_lessthan2$p.stars[4], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(VAF_Category == "<=2%") %>% filter(Gene_Class == "DDR"), 7, 2, 3, model_growth_rate_class_lessthan2$p.value[6], model_growth_rate_class_lessthan2$p.stars[6], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(VAF_Category == ">2%") %>% filter(Gene_Class == "DDR"), 6, 1, 2, model_growth_rate_class_greaterthan2$p.value[3], model_growth_rate_class_greaterthan2$p.stars[3], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(VAF_Category == ">2%") %>% filter(Gene_Class == "DDR"), 6.5, 1, 3, model_growth_rate_class_greaterthan2$p.value[4], model_growth_rate_class_greaterthan2$p.stars[4], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(VAF_Category == ">2%") %>% filter(Gene_Class == "DDR"), 7, 2, 3, model_growth_rate_class_greaterthan2$p.value[6], model_growth_rate_class_greaterthan2$p.stars[6], show_values = TRUE, hide_ns = TRUE, textsize = 6))

extdata_fig2
pdf(paste0(figures_save_path, "ExtFigure2_GrowthRates_VAFCategory.pdf"), width = 14, height = 10)
extdata_fig2
dev.off()
```

# Extended Data Figure 3A - Growth Rate by Cancer Types
```{r extdata_fig3a, message = FALSE, warning = FALSE, fig.width=15, fig.height=8}
df_to_plot <- timepoints %>%
    left_join(
        table_demographics %>% select(DEID, CANCER.DX),
        by = c("DeID"="DEID")
    ) %>%
    mutate(
        CANCER.DX = ifelse(CANCER.DX %in% c("Ovary/Uterus", "Prostate", "Lung/Mesothelioma"), CANCER.DX, "Other")
    ) %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(Gene_Class == "DDR" | Gene_Class == "DTA")

counts <- df_to_plot %>%
    group_by(Cohort, Gene_Class, CANCER.DX) %>%
    summarise(n = n(), .groups = "drop")

extdata_fig3a <- df_to_plot %>%
    ggplot(
        aes(
            x = Cohort,
            y = growth_rate,
            fill = CANCER.DX
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.06), size = 4, position = position_dodge(width = 0.8)) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    scale_color_nejm() +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(2, 0, 0, 1, "cm"),
        axis.text.x = ggtext::element_markdown(angle = 45, hjust = 1, size = 16),
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05)) +
    facet_wrap(~ Gene_Class)
extdata_fig3a
pdf(paste0(figures_save_path, "ExtFigure3A_GrowthRate_CancerTypes.pdf"), width = 14, height = 8)
extdata_fig3a
dev.off()
```

# Extended Data Figure 3B - Growth Rate by Gene no co-mutation
```{r extdata_fig3b, message = FALSE, warning = FALSE, fig.width=15, fig.height=8}
# Which patients have TP53 mutations?
has_tp53_ch <- timepoints %>%
    filter(Gene == "TP53") %>%
    pull(DeID) %>%
    unique()
# Which patients have PPM1D mutations?
has_ppm1d_ch <- timepoints %>%
    filter(Gene == "PPM1D") %>%
    pull(DeID) %>%
    unique()

# These patients ONLY have TP53 mutations and no PPM1D mutations
tp53_only <- setdiff(has_tp53_ch, has_ppm1d_ch)
# These patients ONLY have PPM1D mutations and no TP53 mutations
ppm1d_only <- setdiff(has_ppm1d_ch, has_tp53_ch)

df_to_plot <- timepoints %>% 
    #filter(Gene_Class == "DDR") %>%
    filter(Gene %in% c("TP53", "PPM1D")) %>%
    filter(growth_rate != "Inf" & growth_rate != "-Inf") %>%
    filter(DeID %in% c(tp53_only, ppm1d_only))

model_growth_rate_tp53_ppm1d_only <- purrr::cross_df(list(
    gene = c("TP53", "PPM1D"),
    comparison = c("all", "no_untreated")
)) %>%
    pmap_dfr(function(gene, comparison) {
        print(paste(gene, comparison))
        if (comparison == "all") {
            df_subset <- df_to_plot %>% filter(Gene == gene)
            model <- glm(
                formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                data = df_subset
            ) 
        } else if (comparison == "no_untreated") {
            df_subset <- df_to_plot %>% filter(Gene == gene & Cohort != "Healthy")
            model <- glm(
                formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                data = df_subset
            )
        }
        model %>% 
            sjPlot::get_model_data(type = "est") %>%
            filter(grepl("Cohort", term)) %>%
            mutate(
                term = case_when(
                        term == "CohortCarboplatin" ~ "UntreatedVSCarboplatin",
                        term == "CohortPARPi" ~ ifelse(comparison == "all", "UntreatedVSPARPi", "CarboplatinVSPARPi"),
                        TRUE ~ term
                    ),
                gene = gene, 
                comparison = comparison
            )
    })

counts <- df_to_plot %>%
    group_by(Cohort, Gene) %>%
    summarise(n = n(), .groups = "drop")

extdata_fig3b <- df_to_plot %>%
    ggplot(
        aes(
            x = Gene,
            y = growth_rate,
            fill = Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.06), size = 8, position = position_dodge(width = 0.8)) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(2, 0, 0, 1, "cm")
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05), limit = c(NA, 1.5)) +
    do.call(geom_signif, default_sig(5, 0.75, 1, model_growth_rate_tp53_ppm1d_only$p.value[1], model_growth_rate_tp53_ppm1d_only$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(6, 0.75, 1.25, model_growth_rate_tp53_ppm1d_only$p.value[2], model_growth_rate_tp53_ppm1d_only$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(7.1, 1, 1.25, model_growth_rate_tp53_ppm1d_only$p.value[5], model_growth_rate_tp53_ppm1d_only$p.stars[5], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(5, 1.75, 2, model_growth_rate_tp53_ppm1d_only$p.value[3], model_growth_rate_tp53_ppm1d_only$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(6, 1.75, 2.25, model_growth_rate_tp53_ppm1d_only$p.value[4], model_growth_rate_tp53_ppm1d_only$p.stars[4], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig(7.1, 2, 2.25, model_growth_rate_tp53_ppm1d_only$p.value[6], model_growth_rate_tp53_ppm1d_only$p.stars[6], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6))
extdata_fig3b
pdf(paste0(figures_save_path, "ExtFigure3B_GrowthRate_Gene_no_comutation.pdf"), width = 10, height = 8)
extdata_fig3b
dev.off()
```

# Extended Data Figure 4 - MoChA Comparison of mCA Detection with other Cohorts
```{r extdata_fig4, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
mocha_comp <- rbind(
    ukb_mocha_loh %>%
        group_by(CHR, COPY_CHANGE) %>%
        mutate(COPY_CHANGE = ifelse(COPY_CHANGE == "undetermined", "unknown", COPY_CHANGE)) %>%
        summarise(n = n(), .groups = "drop") %>%
        dplyr::rename(chr = CHR) %>%
        mutate(
            prop = n / sum(n),
            cohort = "UK Biobank"
        ),
    jpb_mocha_terao %>%
        mutate(
            COPY_CHANGE = ifelse(COPY_CHANGE == "undetermined", "unknown", COPY_CHANGE)
        ) %>%
        group_by(chr, COPY_CHANGE) %>%
        summarise(n = n(), .groups = "drop") %>%
        mutate(
            prop = (n / sum(n)),
            cohort = "Biobank Japan"
        ),
    mocha_df %>%
        mutate(
            type = case_when(
                type == "CN-LOH" ~ "neutral",
                type == "Gain" ~ "gain",
                type == "Loss" ~ "loss",
                type == "Undetermined" ~ "unknown",
                TRUE ~ type
            ),
            chrom = sub("chr", "", chrom)
        ) %>%
        filter(type != "" & type != "Missing") %>%
        dplyr::rename(chr = chrom, COPY_CHANGE = type) %>%
        group_by(chr, COPY_CHANGE) %>%
        summarise(n = n(), .groups = "drop") %>%
        mutate(
            prop = (n / sum(n)) *-1,
            cohort = "PARPi/Carbo"
        )
) %>%
    filter(chr != "X" & chr != "Y") %>%
    mutate(
        chr = factor(as.character(chr), levels = as.character(1:23)),
        cohort = factor(cohort, levels = c("UK Biobank", "Biobank Japan", "PARPi/Carbo")),
    )

extdata_fig4a <- mocha_comp %>%
    filter(cohort == "UK Biobank" | cohort == "PARPi/Carbo") %>%
    ggplot(
        aes(
            x = chr,
            y = prop,
            fill = cohort
        )
    ) +
    geom_bar(stat = "identity", position = "stack") +
    scale_x_discrete(breaks = seq(1,22, by = 2)) +
    scale_y_continuous(labels = scales::percent_format(), breaks = c(-0.05, 0, 0.05), limit = c(NA, 0.08)) +
    facet_wrap(~COPY_CHANGE, nrow = 4) +
    labs(
        x = "Chromosome",
        y = "Percent of Cohort",
        fill = "Data"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = c("#CC0000", "#0072B2")) +
    theme(
        plot.margin = margin(0, 0, 0, 1, "cm"),
        axis.text.x = element_text(size = 16),
        legend.text = element_text(size = 16)
    ) 

extdata_fig4b <- mocha_comp %>%
    filter(cohort == "Biobank Japan" | cohort == "PARPi/Carbo") %>%
    ggplot(
        aes(
            x = chr,
            y = prop,
            fill = cohort
        )
    ) +
    geom_bar(stat = "identity", position = "stack") +
    scale_x_discrete(breaks = seq(1,22, by = 2)) +
    scale_y_continuous(labels = scales::percent_format(), breaks = c(-0.05, 0, 0.05), limit = c(NA, NA)) +
    facet_wrap(~COPY_CHANGE, nrow = 4) +
    labs(
        x = "Chromosome",
        y = "",
        fill = "Data"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = c("#D55E00", "#0072B2")) +
    theme(
        plot.margin = margin(0, 0, 0, 1, "cm"),
        axis.text.x = element_text(size = 16),
        legend.text = element_text(size = 16)
    )

extdata_fig4 <- plot_grid(
    extdata_fig4a, extdata_fig4b,
    labels = c("a", "b"),
    label_size = 30,
    ncol = 2
)
extdata_fig4
pdf(paste0(figures_save_path, "ExtFigure4_mCA_Comparison.pdf"), width = 12, height = 14)
extdata_fig4
dev.off()
```

# Extended Data Figure 5A - MoChA CF Growth Rate
```{r extdata_fig5a, message = FALSE, warning = FALSE, fig.width=15, fig.height=8}
df_to_plot <- mocha_timepoints %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(mCA_Detected != "Pre-Pre Treatment Only" & mCA_Detected != "Post-Post Treatment Only") %>%
    filter(event == "mCA")

model_mocha_mca_glm <- rbind(
    glm(
        formula = growth_rate ~ Cohort,
        data = df_to_plot
    ) %>%
    sjPlot::get_model_data(type = "est"),
    glm(
        formula = growth_rate ~ Cohort,
        data = df_to_plot %>%
            filter(Cohort != "Healthy") %>%
            mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi")))
    ) %>%
    sjPlot::get_model_data(type = "est") %>%
    mutate(term = "CarboplatinPARPi")
)

counts <- df_to_plot %>%
    group_by(Cohort) %>%
    summarise(n = n(), .groups = "drop")

extdata_fig5a <- df_to_plot %>%
    ggplot(
        aes(
            x = Cohort,
            y = growth_rate,
            fill = Cohort 
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width = 0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.04), size = 8, position = position_dodge(width = 0.8)) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    facet_wrap(~event) +
    panel_theme_basic +
    scale_fill_nejm() + 
    theme(
        plot.margin = margin(1, 0, 0, 1, "cm"),
        axis.text.x = element_text(angle = 45, hjust = 1),
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.01)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 1.8, 1, 2, model_mocha_mca_glm$p.value[1], model_mocha_mca_glm$p.stars[1], show_values = TRUE, hide_ns = TRUE)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 2.2, 1, 3, model_mocha_mca_glm$p.value[2], model_mocha_mca_glm$p.stars[2], show_values = TRUE, hide_ns = TRUE)) +  
    do.call(geom_signif, default_sig_data(df_to_plot, 2.6, 2, 3, model_mocha_mca_glm$p.value[3], model_mocha_mca_glm$p.stars[3], show_values = TRUE, hide_ns = TRUE))
extdata_fig5a
pdf(paste0(figures_save_path, "ExtFigure5A_MoChA_GrowthRate.pdf"), width = 8, height = 12)
extdata_fig5a
dev.off()
```

# Extended Data Figure 5B - MoChA Proportion of mCA Detected
```{r extdata_fig5b, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
mocha_proportion_detected <- mocha_timepoints %>%
    filter(event == "mCA") %>%
    filter(mCA_Detected != "Pre-Pre Treatment Only" & mCA_Detected != "Post-Post Treatment Only") %>%
    distinct(PatientID, mCA_Detected, Cohort) %>%
    group_by(mCA_Detected, Cohort) %>%
    summarise(total_patients = n(), .groups = "drop")

extdata_fig5b <- mocha_proportion_detected %>%
    group_by(Cohort) %>%
    mutate(
        total_samples = sum(total_patients),
        proportion = total_patients / total_samples
    ) %>%
    ungroup() %>%
    mutate(
        mCA_Detected = factor(mCA_Detected, levels = c("Both Timepoints", "Pre Treatment Only", "Post Treatment Only")),
        Cohort = factor(Cohort, levels = c("Healthy", "Carboplatin", "PARPi"))
    ) %>%
    ggplot(
        aes(
            x = "",
            y = proportion,
            fill = mCA_Detected
        )
    ) +
    geom_bar(width = 1, color = "black", stat = "identity") +
    coord_polar("y", start = 0) +
    geom_text(aes(label = scales::percent(proportion)), position = position_stack(vjust = 0.5), size = 6) +
    labs(
        x = "",
        y = "Percent of Detectable\nAutosomal mCA",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(1, 0, 0, 3, "cm"),
        axis.text.x = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.minor = element_blank()
    ) +
    facet_wrap(~Cohort, ncol = 1)
extdata_fig5b
pdf(paste0(figures_save_path, "ExtFigure5B_MoChA_ProportionDetected.pdf"), width = 10, height = 10)
extdata_fig5b
dev.off()
```

# Extended Data Figure 5C - Pre-Existing DDR Mutations Promote mCA
```{r extdata_fig5c, message = FALSE, warning = FALSE, fig.width=15, fig.height=6}
deid_new_mca <- mocha_timepoints %>%
    filter(event == "mCA" & mCA_Detected == "Post Treatment Only") %>%
    distinct(PatientID) %>%
    pull(PatientID)

# Function to return list of DeIDs who had pre-existing mutations in a given gene
get_deid_pre_from_timepoints <- function(gene) {
    timepoints %>%
        filter(Gene == gene, preVAF > 0) %>%
        distinct(DeID) %>%
        pull(DeID)
}

# List of genes
deid_pre_list <- lapply(c("TP53", "DNMT3A", "TET2", "ASXL1", "PPM1D", "CHEK2"), get_deid_pre_from_timepoints)
names(deid_pre_list) <- paste0(c("TP53", "DNMT3A", "TET2", "ASXL1", "PPM1D", "CHEK2"), "_pre")

gene_map_pre <- setNames(c("TP53", "DNMT3A", "TET2", "ASXL1", "PPM1D", "CHEK2"), paste0(c("tp53", "dnmt3a", "tet2", "asxl1", "ppm1d", "chek2"), "_pre"))

model_pre_existing_gene <- map_dfr(c("TP53", "DNMT3A", "TET2", "ASXL1", "PPM1D", "CHEK2"), function(gene){
    deid_pre <- timepoints %>%
        filter(Gene == gene, preVAF > 0) %>%
        pull(DeID) %>%
        unique()

    mocha_demographics %>% 
        distinct(DeID) %>%
        mutate(
            mca_post = ifelse(DeID %in% deid_new_mca, 1, 0),
            gene_pre = ifelse(DeID %in% deid_pre, 1, 0)
        ) %>%
        select(DeID, mca_post, gene_pre) %>%
        distinct() %>%
        glm(
            formula = mca_post ~ gene_pre,
            data = .,
            family = binomial(link = "logit")
        ) %>%
        sjPlot::get_model_data(type = "est") %>%
        mutate(Gene = gene)
})
model_pre_existing_gene

extdata_fig5c_to_plot <- mocha_demographics %>%
    distinct(DeID) %>%
    mutate(
        mca_post = ifelse(DeID %in% deid_new_mca, 1, 0),
        dnmt3a_pre = ifelse(DeID %in% deid_pre_list$DNMT3A_pre, 1, 0),
        tet2_pre = ifelse(DeID %in% deid_pre_list$TET2_pre, 1, 0),
        asxl1_pre = ifelse(DeID %in% deid_pre_list$ASXL1_pre, 1, 0),
        ppm1d_pre = ifelse(DeID %in% deid_pre_list$PPM1D_pre, 1, 0),
        tp53_pre = ifelse(DeID %in% deid_pre_list$TP53_pre, 1, 0),
        chek2_pre = ifelse(DeID %in% deid_pre_list$CHEK2_pre, 1, 0)
    ) %>%
    pivot_longer(
        cols = all_of(names(gene_map_pre)),
        names_to = "PreGene",
        values_to = "Pre"
    ) %>%
    mutate(
        PreGene = gene_map_pre[PreGene],
        pre_existing = ifelse(Pre == 1, "Yes", "No"),
        PreGene = factor(PreGene, levels = gene_list)
    ) %>%
    group_by(PreGene, pre_existing) %>%
    summarise(
        has_new_mca = sum(mca_post == 1),
        total = n(),
        proportion = has_new_mca / total,
        .groups = "drop"
    )

extdata_fig5c <- extdata_fig5c_to_plot %>%
    ggplot(
        aes(
            x = PreGene,
            y = proportion,
            fill = pre_existing
        )
    ) +
    geom_bar(stat = "identity", position = position_dodge(), color = "black") +
    labs(
        x = "",
        y = "Percent of Patients\nwith New mCA Post Treatment",
        fill = "Pre-existing CH Mutation"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    scale_y_continuous(labels = scales::percent_format(), expand = c(0, 0)) +
    theme(
        plot.margin = margin(1, 0, 0, 1, "cm"),
        axis.text.x = element_text(angle = 45, hjust = 1),
    ) +
    do.call(geom_signif, default_sig_data(extdata_fig5c_to_plot, 0.15, 0.85, 1.15, model_pre_existing_gene$p.value[2], model_pre_existing_gene$p.stars[2], show_values = TRUE, hide_ns = TRUE)) +
    do.call(geom_signif, default_sig_data(extdata_fig5c_to_plot, 0.15, 1.85, 2.15, model_pre_existing_gene$p.value[3], model_pre_existing_gene$p.stars[3], show_values = TRUE, hide_ns = TRUE)) +
    do.call(geom_signif, default_sig_data(extdata_fig5c_to_plot, 0.15, 2.85, 3.15, model_pre_existing_gene$p.value[4], model_pre_existing_gene$p.stars[4], show_values = TRUE, hide_ns = TRUE)) +
    do.call(geom_signif, default_sig_data(extdata_fig5c_to_plot, 0.1, 3.85, 4.15, model_pre_existing_gene$p.value[5], model_pre_existing_gene$p.stars[5], show_values = TRUE, hide_ns = TRUE)) +
    do.call(geom_signif, default_sig_data(extdata_fig5c_to_plot, 0.11, 4.85, 5.15, model_pre_existing_gene$p.value[1], model_pre_existing_gene$p.stars[1], show_values = TRUE, hide_ns = TRUE)) +
    do.call(geom_signif, default_sig_data(extdata_fig5c_to_plot, 0.1, 5.85, 6.15, model_pre_existing_gene$p.value[6], model_pre_existing_gene$p.stars[6], show_values = TRUE, hide_ns = TRUE))
extdata_fig5c
pdf(paste0(figures_save_path, "ExtFigure5C_PreExisting_CH_Mutation.pdf"), width = 12, height = 8)
extdata_fig5c
dev.off()
```

# Extended Data Figure 6 - mCA overlap with CH Genes
```{r extdata_fig6d, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
# DDR Genes - TP53, PPM1D, and CHEK2
# TP53 - 17p13.1 - chr17:7,668,421-7,687,490 - chr17:7,669,609-7,676,594
# PPM1D - 17q23.2 - chr17:60,600,193-60,666,280 - chr17:60,600,415-60,663,552
# CHEK2 - 22q12.1 -  chr22:28,687,743-28,741,820 - chr22:28,687,897-28,734,721

# Maybe check BRCA1/2 as well?
# BRCA1 - 17q21.31 - chr17:43,044,295-43,125,364 - chr17:43,045,678-43,124,096
# BRCA2 - 13q13.1 - chr13:32,315,508-32,400,268 - chr13:32,316,461-32,398,770

mocha_df <- mocha_df %>%
    mutate(
        chrom_arm = case_when(
            (p_arm == "N" | p_arm == "C") & (q_arm == "Y" | q_arm == "T") ~ paste0(chrom, "q"),
            (p_arm == "Y" | p_arm == "T") & (q_arm == "N" | q_arm == "C") ~ paste0(chrom, "p"),
            (p_arm == "Y" | p_arm == "T") & (q_arm == "Y" | q_arm == "T") ~ chrom,
            TRUE ~ NA_character_
        )
    )

# These just have pre and post
mocha_have_pre_post <- mocha_demographics %>% group_by(DeID) %>% summarise(n = n()) %>% filter(n == 2) %>% pull(DeID)
# These will have up to post post
mocha_have_up_to_post_post <- mocha_demographics %>% group_by(DeID) %>% summarise(n = n()) %>% filter(n > 2 & n < 5) %>% pull(DeID)
# These are special case
mocha_special_case <- mocha_demographics %>% group_by(DeID) %>% summarise(n = n()) %>% filter(n == 5) %>% pull(DeID)

whereincycle_info <- mocha_demographics %>%
    mutate(
        whereincycle = case_when(
            DeID %in% mocha_have_pre_post ~ ifelse(whichdraw == 1, "pre", "post"),
            DeID %in% mocha_have_up_to_post_post ~ case_when(
                whichdraw == 1 ~ "pre-pre",
                whichdraw == 2 ~ "pre",
                whichdraw == 3 ~ "post",
                whichdraw == 4 ~ "post-post",
                TRUE ~ NA_character_
            ),
            DeID == "115337" ~ case_when(
                whichdraw == 1 ~ "pre-pre",
                whichdraw == 2 ~ "pre",
                whichdraw == 3 ~ "post",
                whichdraw == 4 ~ "post-post"
            ),
            DeID == "1537527" ~ case_when(
                whichdraw == 1 ~ "pre-pre",
                whichdraw == 2 ~ "pre",
                whichdraw == 3 ~ "post",
                whichdraw == 4 ~ "pre",
                whichdraw == 5 ~ "post",
            ),
            DeID == "1540488" ~ case_when(
                whichdraw == 1 ~ "pre-pre",
                whichdraw == 2 ~ "pre",
                whichdraw == 3 ~ "post",
                whichdraw == 4 ~ "post-post"
            ),
            DeID == "1592759" ~ case_when(
                whichdraw == 1 ~ "pre",
                whichdraw == 2 ~ "post",
                whichdraw == 3 ~ "pre",
                whichdraw == 4 ~ "post"
            )
        )
    ) %>%
    select(DeID, SampleDeID, whereincycle, Cohort) %>%
    unique()

num_mutations_per_person_mocha <- mocha_df %>%
    mutate(
        type = case_when(
            type == "CN-LOH" ~ "Copy Neutral LOH",
            type == "Gain" ~ "Gain",
            type == "Loss" ~ "Loss",
            type == "Undetermined" ~ "Unknown",
            TRUE ~ type
        ),
        chrom = sub("chr", "", chrom),
        chrom_arm_type = paste0(chrom_arm, "_", type)
    ) %>%
    filter(type != "" & type != "Missing") %>%
    left_join(
        whereincycle_info,
        by = c("DeID" = "DeID", "Sample_DeID" = "SampleDeID")
    ) %>%
    filter(whereincycle == "post") %>%
    group_by(DeID, chrom_arm_type, Cohort) %>%
    summarise(n = n()) %>%
    pivot_wider(names_from = chrom_arm_type, values_from = n, values_fill = 0) %>%
    ungroup()

# For each person, what are the mutations they have in each chrom arm, and what is their treatment status?
mut_table_mocha <- mocha_demographics %>%
    filter(Duplicate == 0) %>%
    select(DeID, SampleDeID, Cohort, AGE, Sex_Reported, Ancestry, Cohort) %>%
    left_join(
        whereincycle_info,
        by = c("DeID" = "DeID", "SampleDeID" = "SampleDeID", "Cohort" = "Cohort")
    ) %>%
    filter(!is.na(whereincycle)) %>%
    filter(whereincycle == "post") %>%
    left_join(num_mutations_per_person_mocha, by = c("DeID" = "DeID", "Cohort" = "Cohort")) %>%
    select(-SampleDeID, -whereincycle) %>%
    group_by(DeID, AGE, Sex_Reported, Ancestry, Cohort) %>%
    summarise_if(is.numeric, function(x) sum(x != 0, na.rm = TRUE))

mocha_treatment_prop <- mut_table_mocha %>%
    group_by(Cohort) %>%
    dplyr::select(-AGE, -Sex_Reported, -Ancestry) %>%
    summarise_if(is.numeric, sum, na.rm = TRUE) %>%
    pivot_longer(cols = -Cohort, names_to = "ChromArmType", values_to = "n") %>%
    ungroup() %>%
    left_join(
        mut_table_mocha %>%
            group_by(Cohort) %>%
            summarise(total_patients = n())
    ) %>%
    mutate(
        Proportion = n / total_patients,
        #Type = factor(Type, levels = c("unknown", "loss", "neutral", "gain"))
        #Gene = factor(Gene, levels = c(gene_list)),
        #Treatment = ifelse(anytreatment == "Treatment", "Post-Treatment", "Untreated"),
        #Treatment = factor(Treatment, levels = c("Untreated", "Post-Treatment"))
    ) %>%
    separate(ChromArmType, into = c("chrom_arm", "type"), sep = "_")

extdata_fig6 <- mocha_treatment_prop %>%
    filter(!grepl("chrX", chrom_arm)) %>%
    filter(!is.na(chrom_arm)) %>%
    mutate(Cohort = factor(Cohort, levels = c("Healthy", "Carboplatin", "PARPi"))) %>%
    complete(Cohort, chrom_arm, type, fill = list(n = 0, total_patients = 0, Proportion = 0)) %>%
    mutate(
        chrom_arm = factor(chrom_arm, levels = c("chr1p", "chr1q", "chr2p", "chr2q", "chr3p", "chr3q", "chr4p", "chr4q", "chr5p", "chr5q", "chr6p", "chr6q", "chr7p", "chr7q", "chr8p", "chr8q", "chr9p", "chr9q", "chr10p", "chr10q", "chr11p", "chr11q", "chr12p", "chr12q", "chr13p", "chr13q", "chr14p", "chr14q", "chr15p", "chr15q", "chr16p", "chr16q", "chr17p", "chr17q", "chr18p", "chr18q", "chr19p", "chr19q", "chr20p", "chr20q", "chr21p", "chr21q", "chr22p", "chr22q"))
    ) %>%
    filter(!is.na(chrom_arm)) %>%
    ggplot(
        aes(
            x = chrom_arm,
            y = Proportion,
            fill = Cohort
        )
    ) +
    geom_bar(stat = "identity", position = "dodge", color = "black") +
    labs(
        x = "Type of mCA",
        y = "Proportion of Patients with mCA",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    scale_y_continuous(labels = scales::percent_format(), expand = c(0, 0)) +
    theme(
        plot.margin = margin(1, 0, 0, 1, "cm"),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(angle = 45, hjust = 1),
    ) +
    facet_wrap(~type, ncol = 1)

extdata_fig6
pdf(paste0(figures_save_path, "ExtFigure6_mCA_ProportionByCohort.pdf"), width = 12, height = 10)
extdata_fig6
dev.off()

# Statistics for the 4 positions
rbind(
    glm(
        data = mut_table_mocha %>%
            filter(Cohort != "PARPi") %>%
            mutate(Cohort = factor(Cohort, levels = c("Healthy", "Carboplatin"))),
        formula = chr13q_Loss ~ Cohort + AGE + Sex_Reported + Ancestry,
        family = binomial(link = "logit")
    ) %>% sjPlot::get_model_data(type = "est") %>%
        filter(grepl("Cohort", term)) %>%
        mutate(
            term = "Healthy vs. Carboplatin",
            chrom_arm_type = "chr13q_loss"
        ),
    glm(
        data = mut_table_mocha %>%
            filter(Cohort != "PARPi") %>%
            mutate(Cohort = factor(Cohort, levels = c("Healthy", "Carboplatin"))),
        formula = `chr13q_Copy Neutral LOH` ~ Cohort + AGE + Sex_Reported + Ancestry,
        family = binomial(link = "logit")
    ) %>% sjPlot::get_model_data(type = "est") %>%
        filter(grepl("Cohort", term)) %>%
        mutate(
            term = "Healthy vs. Carboplatin",
            chrom_arm_type = "chr13q_neutral"
        ),
    glm(
        data = mut_table_mocha %>%
            filter(Cohort != "Healthy") %>%
            mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi"))),
        formula = `chr14q_Copy Neutral LOH` ~ Cohort + AGE + Sex_Reported + Ancestry,
        family = binomial(link = "logit")
    ) %>% sjPlot::get_model_data(type = "est") %>%
        filter(grepl("Cohort", term)) %>%
        mutate(
            term = "Carboplatin vs. PARPi",
            chrom_arm_type = "chr14q_neutral"
        ),
    glm(
        data = mut_table_mocha %>%
            filter(Cohort != "Carboplatin") %>%
            mutate(Cohort = factor(Cohort, levels = c("Healthy", "PARPi"))),
        formula = chr17p_Loss ~ Cohort + AGE + Sex_Reported + Ancestry,
        family = binomial(link = "logit")
    ) %>% sjPlot::get_model_data(type = "est") %>%
        filter(grepl("Cohort", term)) %>%
        mutate(
            term = "Healthy vs. PARPi",
            chrom_arm_type = "chr17p_loss"
        )
)
```

# Extended Data Figure 7 - Platinum Treatment Expands Tp53 Mutant Cells
```{r extdata_fig7, message = FALSE, warning = FALSE, fig.width=15, fig.height=20}
extdata_fig7a <- make_mouse_cell_plot(
    mouse_data[["ExtDataFigure 7"]] %>%
        mutate(Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib", "Olaparib"))),
    cell_col = "Granulocytes",
    title = "Granulocytes",
    y_label = ""
    #y_label = expression(atop("%Trp53"^"R172H/+"~"Cells", "(Normalized to 0-week)"))
)
extdata_fig7a <- add_significance_annotation(extdata_fig7a, "P<0.0001", 13.5, 2.05, 1.08, size_text = 6)
pdf(paste0(figures_save_path, "ExtFigure7A_Platinum_Treatment_Tp53_Mutant_Cells_Granulocytes.pdf"), extdata_fig7a, width = 12, height = 8)
extdata_fig7a
dev.off()

extdata_fig7b <- make_mouse_cell_plot(
    mouse_data[["ExtDataFigure 7"]] %>%
        mutate(Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib", "Olaparib"))),
    cell_col = "B_Cells",
    title = "B Cells",
    y_label = ""
    #y_label = expression(atop("%Trp53"^"R172H/+"~"Cells", "(Normalized to 0-week)"))
)
extdata_fig7b <- add_significance_annotation(extdata_fig7b, "P=0.0006", 13.5, 1.89, 1.17, size_text = 6)
pdf(paste0(figures_save_path, "ExtFigure7B_Platinum_Treatment_Tp53_Mutant_Cells_BCells.pdf"), extdata_fig7b, width = 12, height = 8)
extdata_fig7b
dev.off()

extdata_fig7c <- make_mouse_cell_plot(
    mouse_data[["ExtDataFigure 7"]] %>%
        mutate(Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib", "Olaparib"))),
    cell_col = "Monocytes",
    title = "Monocytes",
    y_label = "",
    #y_label = expression(atop("%Trp53"^"R172H/+"~"Cells", "(Normalized to 0-week)")),
    y_limits = c(0, 3.0),
    x_limits = as.character(0:14)
)
extdata_fig7c <- add_significance_annotation(extdata_fig7c, "P<0.0001", 14, 2.08, 1.17, size_text = 6)
extdata_fig7c <- add_significance_annotation(extdata_fig7c, "P=0.0488", 13.5, 1.72, 1.17, size_text = 6)
pdf(paste0(figures_save_path, "ExtFigure7C_Platinum_Treatment_Tp53_Mutant_Cells_Monocytes.pdf"), extdata_fig7c, width = 12, height = 8)
extdata_fig7c
dev.off()

extdata_fig7 <- plot_grid(
  ggdraw() + annotate("text", x = 0.5, y = 0.5, label = "CD45.2 Cells (Normalized to 0-Week)", size = 8, angle = 90),
  plot_grid(extdata_fig7a, extdata_fig7b, extdata_fig7c, ncol = 1),
  ncol = 2,
  rel_widths = c(0.5, 10),
  rel_heights = c(1, 1)
)
extdata_fig7
ggsave(paste0(figures_save_path, "ExtFigure7_Platinum_Treatment_Tp53_Mutant_Cells.png"), extdata_fig7, width = 15, height = 12, units = "in", dpi = 300)
```

# Extended Data Figure 8 - TP53-Mutants have Decreased Engraftment
```{r extdata_fig8, message = FALSE, warning = FALSE, fig.width=20, fig.height=15}
extdata_fig8 <- mouse_data[["ExtDataFigure 8"]] %>%
    group_by(Cohort, Week) %>%
    summarise(mean_value = mean(CD45.2_Cells), sd_value = sd(CD45.2_Cells), sem_value = sd(CD45.2_Cells, na.rm = TRUE)/sqrt(n())) %>%
    ggplot(
        aes(
        x = factor(Week),
        y = mean_value,
        fill = Cohort,
        color = Cohort,
        group = Cohort
        )
    ) +
    geom_point(size = 6) +
    geom_line() +
    geom_errorbar(
        aes(
            ymin = mean_value - sem_value,
            ymax = mean_value + sem_value
        ),
        width = 0.5
    ) +
    labs(
        x = "Weeks Post-Transplant",
        y = expression("%"~Trp53^"R172H/+"~Cells),
        fill = "Cohort",
        title = "Leukocyte Chimerism"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    scale_color_nejm() +
    theme(
        plot.margin = margin(1, 1, 1, 1, "cm"),
        plot.title = element_text(hjust = 0.5)
    ) +
    ylim(NA, 50) +
    scale_x_discrete(limits = as.character(0:17), expand = c(0, 0.5), breaks = c(0, 4, 8, 12, 16))
extdata_fig8
pdf(paste0(figures_save_path, "ExtFigure8_TP53_Mutants_Decreased_Engraftment.pdf"), extdata_fig8, width = 8, height = 6)
extdata_fig8
dev.off()
```

# Extended Data Figure 9 - Mutant TP53 Cells fail to expand
```{r extdata_fig9, message = FALSE, warning = FALSE, fig.width=15, fig.height=20}
extdata_fig9a <- make_mouse_cell_plot(
    mouse_data[["ExtDataFigure 9"]] %>%
        mutate(
            Cohort = case_when(
                Cohort == "BRCA1 Vehicle" ~ "Brca1 fl/+ Vehicle",
                Cohort == "BRCA1 Cisplatin" ~ "Brca1 fl/+ Cisplatin",
                Cohort == "BRCA1 Talazoparib" ~ "Brca1 fl/+ Talazoparib"
            ),
            Cohort = factor(Cohort, levels = c("Brca1 fl/+ Vehicle", "Brca1 fl/+ Cisplatin", "Brca1 fl/+ Talazoparib"))
        ),
    cell_col = "Granulocytes",
    title = "Granulocytes"
)
pdf(paste0(figures_save_path, "ExtFigure9A_Granulocytes.pdf"), width = 12, height = 8)
extdata_fig9a
dev.off()

extdata_fig9b <- make_mouse_cell_plot(
    mouse_data[["ExtDataFigure 9"]] %>%
        mutate(
            Cohort = case_when(
                Cohort == "BRCA1 Vehicle" ~ "Brca1 fl/+ Vehicle",
                Cohort == "BRCA1 Cisplatin" ~ "Brca1 fl/+ Cisplatin",
                Cohort == "BRCA1 Talazoparib" ~ "Brca1 fl/+ Talazoparib"
            ),
            Cohort = factor(Cohort, levels = c("Brca1 fl/+ Vehicle", "Brca1 fl/+ Cisplatin", "Brca1 fl/+ Talazoparib"))
        ),
    cell_col = "B_Cells",
    title = "B Cells"
)
pdf(paste0(figures_save_path, "ExtFigure9B_BCells.pdf"), width = 12, height = 8)
extdata_fig9b
dev.off()

extdata_fig9c <- make_mouse_cell_plot(
    mouse_data[["ExtDataFigure 9"]] %>%
        mutate(
            Cohort = case_when(
                Cohort == "BRCA1 Vehicle" ~ "Brca1 fl/+ Vehicle",
                Cohort == "BRCA1 Cisplatin" ~ "Brca1 fl/+ Cisplatin",
                Cohort == "BRCA1 Talazoparib" ~ "Brca1 fl/+ Talazoparib"
            ),
            Cohort = factor(Cohort, levels = c("Brca1 fl/+ Vehicle", "Brca1 fl/+ Cisplatin", "Brca1 fl/+ Talazoparib"))
        ),
    cell_col = "Monocytes",
    title = "Monocytes",
    y_limits = c(0, 8.5)
)
pdf(paste0(figures_save_path, "ExtFigure9C_Monocytes.pdf"), width = 12, height = 8)
extdata_fig9c
dev.off()
```

# Extended Data Figure 10 - Anemia Response to Talazoparib
```{r extdata_fig10, message = FALSE, warning = FALSE, fig.width=15, fig.height=20}
df_to_plot <- mouse_data[["ExtDataFigure 10a"]] %>%
    mutate(
        BloodCount = str_squish(BloodCount),               # remove double spaces
        BloodCount = factor(BloodCount, levels = c("WBC (K/uL)", "RBC (M/uL)", "Hb (g/dL)")),
        Drug = stringr::str_remove(Treatment, "^(WT\\s+|Brca fl/\\+\\s+)"),
        Treatment = str_squish(Treatment),               # remove double spaces
        Treatment = factor(Treatment, levels = c("WT Vehicle", "WT Cisplatin", "WT Talazoparib", "Brca fl/+ Vehicle", "Brca fl/+ Cisplatin", "Brca fl/+ Talazoparib"))
    )

df_summary <- df_to_plot %>%
    group_by(BloodCount, Treatment) %>%
    summarise(
        mean = mean(Value, na.rm = TRUE),
    se = sd(Value, na.rm = TRUE)/sqrt(n()),
    .groups = "drop"
  )

extdata_fig10a <- ggplot() +
    geom_hline(yintercept = 11, linetype = "dotted") +  # Hb low
    geom_hline(yintercept = 7, linetype = "dotted") +   # RBC low
    geom_bar(data = df_summary, aes(x = BloodCount, y = mean, fill = Treatment), stat = "identity", position = position_dodge(width = 0.7), width = 0.7, color = "black") +
    geom_errorbar(data = df_summary, aes(x = BloodCount, ymin = mean - se, ymax = mean + se, group = Treatment), position = position_dodge(width = 0.7), width = 0.2) +
    geom_point(data = df_to_plot, aes(x = BloodCount, y = Value, shape = Treatment), position = position_jitterdodge(jitter.width=0.15, dodge.width=0.7), size = 2, color = "black") +
    labs(
        x = "",
        y = "",
        fill = "Cohort",
        shape = "Cohort",
    ) +
    panel_theme_basic +
    scale_shape_manual(values = c(15, 16, 17, 0, 1, 2)) +
    scale_fill_manual(values = c("WT Vehicle" = "#BC3C29FF", "WT Cisplatin" = "#0072B2FF", "WT Talazoparib" = "#E18727FF", "Brca fl/+ Vehicle" = "#BC3C29FF", "Brca fl/+ Cisplatin" = "#0072B2FF", "Brca fl/+ Talazoparib" = "#E18727FF")) +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(1, 1, 0, 0, "cm")
    ) +
    ylim(0, 30) +
    # WBC
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 0.95, xmax = 1.32, annotations = "P=0.0052", tip_length = 0.02, y_position = 20, textsize = 6, size = 1) +
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 1.05, xmax = 1.17, annotations = "P=0.0004", tip_length = 0.02, y_position = 18, textsize = 6, size = 1) +
    # RBC
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 2.17, xmax = 2.32, annotations = "P<0.0001", tip_length = 0.02, y_position = 11, textsize = 6, size = 1) +
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 2.07, xmax = 2.32, annotations = "P<0.0001", tip_length = 0.02, y_position = 13, textsize = 6, size = 1) +
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 1.95, xmax = 2.32, annotations = "P<0.0001", tip_length = 0.02, y_position = 15, textsize = 6, size = 1) +
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 1.75, xmax = 2.32, annotations = "P<0.0001", tip_length = 0.02, y_position = 17, textsize = 6, size = 1) +
    # Hb
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 3.17, xmax = 3.32, annotations = "P<0.0001", tip_length = 0.02, y_position = 13, textsize = 6, size = 1) +
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 3.05, xmax = 3.17, annotations = "P=0.0092", tip_length = 0.02, y_position = 17, textsize = 6, size = 1) +
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 3.05, xmax = 3.32, annotations = "P<0.0001", tip_length = 0.02, y_position = 19, textsize = 6, size = 1) +
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 2.95, xmax = 3.32, annotations = "P<0.0001", tip_length = 0.02, y_position = 21, textsize = 6, size = 1) +
    geom_signif(data = df_to_plot, aes(x = BloodCount, y = Value, group = Treatment), xmin = 2.75, xmax = 3.32, annotations = "P<0.0001", tip_length = 0.02, y_position = 23, textsize = 6, size = 1)
extdata_fig10a
pdf(paste0(figures_save_path, "ExtFigure10A_Anemia_Response_Talazoparib.pdf"), width = 14, height = 8)
extdata_fig10a
dev.off()

fit <- survfit(
    Surv(Days, Status) ~ Cohort, 
    data = mouse_data[["ExtDataFigure 10b"]] %>%
    mutate(
        Cohort = str_squish(Cohort),
        Cohort = case_when(
            Cohort == "WT:R172H Vehicle" ~ "WT Vehicle",
            Cohort == "WT:R172H Cisplatin" ~ "WT Cisplatin",
            Cohort == "WT:R172H Talazoparib" ~ "WT Talazoparib",
            Cohort == "BRCA1:R172H Vehicle" ~ "Brca fl/+ Vehicle",
            Cohort == "BRCA1:R172H Cisplatin" ~ "Brca fl/+ Cisplatin",
            Cohort == "BRCA1:R172H Talazoparib" ~ "Brca fl/+ Talazoparib",
        ),
        Cohort = factor(Cohort, levels = c("WT Vehicle", "WT Cisplatin", "WT Talazoparib", "Brca fl/+ Vehicle", "Brca fl/+ Cisplatin", "Brca fl/+ Talazoparib"))
    )
  )

cohort_levels <- c(
  "WT Vehicle", "WT Cisplatin", "WT Talazoparib",
  "Brca fl/+ Vehicle", "Brca fl/+ Cisplatin", "Brca fl/+ Talazoparib"
)
cohort_colors <- c("#BC3C29FF", "#0072B2FF", "#E18727FF", "#BC3C29FF", "#0072B2FF", "#E18727FF")
cohort_linetypes <- c("solid", "solid", "solid", "dashed", "dashed", "dashed")
extdata_fig10b <- ggsurvplot(
    fit,
    linetype = cohort_linetypes,
    palette = cohort_colors,
    legend = "right",
    legend.title = "Cohort",
    legend.labs = c(
        "WT Vehicle", "WT Cisplatin", "WT Talazoparib",
        "Brca fl/+ Vehicle", "Brca fl/+ Cisplatin", "Brca fl/+ Talazoparib"
    ),
    xlab = "Days (post-transplant)",
    ylab = "Overall Survival Probability",
    title = ""
)
extdata_fig10b <- extdata_fig10b$plot + 
    annotate(geom = "rect", xmin = 44, xmax = 72, ymin = 0, ymax = 0.05, fill = "black") +
    geom_text(data = data.frame(x = 58, y = 0.1, label = "Treatment"), aes(x = x, y = y, label = label), color = "black", size = 8) +
    annotate("text", x = 150 - 5, y = 0.76/2.05, label = "P=0.0012", size = 6) +
    annotate("segment", x = 150, xend = 150, y = 0.32, yend = 0.44, size = 1) +
    annotate("segment", x = 150, xend = 160, y = 0.32, yend = 0.32, size = 1) +
    annotate("segment", x = 150, xend = 160, y = 0.44, yend = 0.44, size = 1) +
    panel_theme_basic + 
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(1, 1, 1, 1, "cm")
    ) +
    guides(
      colour = guide_legend(keywidth = unit(2.2, "cm"), override.aes = list(size = 1.5, linetype = cohort_linetypes)),
      linetype = guide_legend(keywidth = unit(2.2, "cm"), override.aes = list(size = 1.5, linetype = cohort_linetypes))
    ) +
    theme(
      legend.key.width = unit(2.2, "cm"),
      legend.key.height = unit(0.6, "cm")
    )
extdata_fig10b
pdf(paste0(figures_save_path, "ExtFigure10B_Anemia_Response_Talazoparib_Survival.pdf"), width = 14, height = 8)
extdata_fig10b
dev.off()
```

# Supp Figure 1A and B - Statistics
```{r suppfig_fig1ab_stats, message = FALSE, warning = FALSE}
model_list_tp53 <- list(
    "TP53 CH Unadjusted" = TP53_CH ~ ind_parp_inhibitor + ind_cytotoxic_therapy + ind_radiotherapy + XRT + ind_immune_therapy + ind_non_parp_targeted_therapy + age + smoke_bin + race_b + timedx_impact,
    "TP53 CH Adjusted for Cytotoxic Therapy" = TP53_CH ~ ind_parp_inhibitor + ind_platinum + ind_topoisomerase_ii_inh + ind_microtubule_damaging + ind_topoisomerase_i_inhi + ind_taxane + ind_antimetabolite + ind_alkylating_agent + ind_radiotherapy + ind_targeted_therapy + XRT + ind_immune_therapy + ind_non_parp_targeted_therapy + age + smoke_bin + race_b + timedx_impact,
    "TP53 CH Adjusted for Amount of Cytotoxic Therapy" = TP53_CH ~ pct_parp_inhibitor + 
      pct_carboplatin + pct_cisplatin + pct_oxaliplatin + pct_anthracycline + pct_epipodophyllotoxins + pct_cytotoxic_therapy_ot + pct_topoisomerase_i_inhi + pct_topoisomerase_ii_inh + 
      pct_microtubule_damaging +  pct_taxane + pct_antimetabolite + pct_alkylating_agent + pct_radiotherapy + pct_targeted_therapy + pct_immune_therapy + 
      eqd_10_t + age + smoke_bin + race_b + timedx_impact
)

model_list_ppm1d <- list(
    "PPM1D CH Unadjusted" = PPM1D_CH ~ ind_parp_inhibitor + ind_cytotoxic_therapy + ind_radiotherapy + XRT + ind_immune_therapy + ind_non_parp_targeted_therapy + age + smoke_bin + race_b + timedx_impact,
    "PPM1D CH Adjusted for Cytotoxic Therapy" = PPM1D_CH ~ ind_parp_inhibitor + ind_platinum + ind_topoisomerase_ii_inh + ind_microtubule_damaging + ind_topoisomerase_i_inhi + ind_taxane + ind_antimetabolite + ind_alkylating_agent + ind_radiotherapy + ind_targeted_therapy + XRT + ind_immune_therapy + ind_non_parp_targeted_therapy + age + smoke_bin + race_b + timedx_impact,
    "PPM1D CH Adjusted for Amount of Cytotoxic Therapy" = PPM1D_CH ~ pct_parp_inhibitor + 
      pct_carboplatin + pct_cisplatin + pct_oxaliplatin + pct_anthracycline + pct_epipodophyllotoxins + pct_cytotoxic_therapy_ot + pct_topoisomerase_i_inhi + pct_topoisomerase_ii_inh + 
      pct_microtubule_damaging +  pct_taxane + pct_antimetabolite + pct_alkylating_agent + pct_radiotherapy + pct_targeted_therapy + pct_immune_therapy + 
      eqd_10_t + age + smoke_bin + race_b + timedx_impact
)

model_list_chek2 <- list(
    "CHEK2 CH Unadjusted" = CHEK2_CH ~ ind_parp_inhibitor + ind_cytotoxic_therapy + ind_radiotherapy + XRT + ind_immune_therapy + ind_non_parp_targeted_therapy + age + smoke_bin + race_b + timedx_impact,
    "CHEK2 CH Adjusted for Cytotoxic Therapy" = CHEK2_CH ~ ind_parp_inhibitor + ind_platinum + ind_topoisomerase_ii_inh + ind_microtubule_damaging + ind_topoisomerase_i_inhi + ind_taxane + ind_antimetabolite + ind_alkylating_agent + ind_radiotherapy + ind_targeted_therapy + XRT + ind_immune_therapy + ind_non_parp_targeted_therapy + age + smoke_bin + race_b + timedx_impact,
    "CHEK2 CH Adjusted for Amount of Cytotoxic Therapy" = CHEK2_CH ~ pct_parp_inhibitor + 
      pct_carboplatin + pct_cisplatin + pct_oxaliplatin + pct_anthracycline + pct_epipodophyllotoxins + pct_cytotoxic_therapy_ot + pct_topoisomerase_i_inhi + pct_topoisomerase_ii_inh + 
      pct_microtubule_damaging +  pct_taxane + pct_antimetabolite + pct_alkylating_agent + pct_radiotherapy + pct_targeted_therapy + pct_immune_therapy + 
      eqd_10_t + age + smoke_bin + race_b + timedx_impact
)

msk_models_ch <- map(c(model_list_tp53, model_list_ppm1d, model_list_chek2), function(formula){
    glm(
        formula = formula,
        family = binomial(link = "logit"),
        data = msk_df
    ) %>%
    sjPlot::get_model_data(type = "est")
})
```

# Supp Figure 1A - Logistic Regression Analysis of Therapy on DDR CH Mutations
```{r suppfig_fig1a, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
supp_fig1a <- rbind(
    msk_models$Unadjusted %>% mutate(Classification = "DDR CH"),
    msk_models_ch$`TP53 CH Unadjusted` %>% mutate(Classification = "TP53 CH"),
    msk_models_ch$`PPM1D CH Unadjusted` %>% mutate(Classification = "PPM1D CH")#,
    #msk_models_ch$`CHEK2 CH Unadjusted` %>% mutate(Classification = "CHEK2 CH")    # There are too few
) %>%
    filter(str_detect(term, "ind_|XRT")) %>%
    mutate(
        term = case_when(
            term == "ind_parp_inhibitor" ~ "PARP Inhibitor",
            term == "ind_cytotoxic_therapy" ~ "Cytotoxic Therapy",
            term == "ind_radiotherapy" ~ "Radionucleotide Therapy",
            term == "XRT" ~ "External Beam Radiation",
            term == "ind_immune_therapy" ~ "Immune Therapy",
            term == "ind_non_parp_targeted_therapy" ~ "Other Targeted Therapy",
            TRUE ~ term
        ),
        term = factor(term, levels = c("Other Targeted Therapy",
                                    "Immune Therapy",
                                    "External Beam Radiation",
                                    "Radionucleotide Therapy",
                                    "Cytotoxic Therapy",
                                    "PARP Inhibitor")),
        Classification = factor(Classification, levels = c("DDR CH", "TP53 CH", "PPM1D CH", "CHEK2 CH")),
        p.label = ifelse(p.stars != "", paste0("P=",format(p.value, digits = 2)), "")
    ) %>%
    select(term, Classification, estimate, std.error, conf.low, conf.high, p.value, p.stars, p.label) %>%
    filter(!(term == "Radionucleotide Therapy" & Classification == "TP53 CH")) %>% # Remove Radionucleotide Therapy for TP53 CH because the confidence interval is too wide to be visualized on the same plot
    ggplot(
        aes(
            x = term,
            y = estimate,
            ymin = conf.low,
            ymax = conf.high,
            col = Classification,
            fill = Classification
        )
    ) +
    geom_point(position = position_dodge(width = 0.7), size = 5) +
    geom_errorbar(position = position_dodge(width = 0.7), width = 0.4, linewidth = 1) +
    #geom_text(aes_string(label = "p.stars", vjust = 0.1), size = 8, position = position_dodge(width = 0.7), color = "black") +
    geom_text(aes(label = p.label, vjust = -0.8), size = 4, position = position_dodge(width = 0.7), color = "black") +
    geom_hline(yintercept = 1, color = "black", linetype = "solid") +
    coord_flip() +
    scale_color_nejm() +
    scale_y_log10(breaks = c(0.1, 0.2, 0.3, 0.5, 1, 2, 3, 5, 10)) +
    #scale_y_log10(limits = c(NA, NA), breaks = c(1, 2, 3, 5, 10), labels = scales::label_number(accuracy = 1L)) +
    labs(
        y = "Odds Ratio of DDR CH",
        x = "",
        title = "",
        color = "Gene",
        fill = "Gene"
    ) +
    panel_theme_basic +
    theme(
        panel.grid.major.x = element_line(color = alpha("grey", 0.8), size = 0.5, linetype = "solid"),
        axis.text.x = ggtext::element_markdown(size = 18),
        axis.text.y = element_text(size = 18)
    )
supp_fig1a
```

# Supp Figure 1B - Logistic Regression Analysis of PARP Inhibitor on DDR CH Mutations Adjusted
```{r suppfig_fig1b, message = FALSE, warning = FALSE, fig.width=16, fig.height=6}
supp_fig1b <- rbind(
    msk_models$`Adjusted for Cytotoxic Therapy` %>% filter(term == "ind_parp_inhibitor") %>% mutate(Classification = "DDR CH"),
    msk_models_ch$`TP53 CH Adjusted for Cytotoxic Therapy` %>% filter(term == "ind_parp_inhibitor") %>% mutate(Classification = "TP53 CH"),
    msk_models_ch$`PPM1D CH Adjusted for Cytotoxic Therapy` %>% filter(term == "ind_parp_inhibitor") %>% mutate(Classification = "PPM1D CH"),
    #msk_models_ch$`CHEK2 CH Adjusted for Cytotoxic Therapy` %>% filter(term == "ind_parp_inhibitor") %>% mutate(Classification = "CHEK2 CH"),
    msk_models$`Adjusted for Amount of Cytotoxic Therapy` %>% filter(term == "pct_parp_inhibitor") %>% mutate(Classification = "DDR CH"),
    msk_models_ch$`TP53 CH Adjusted for Amount of Cytotoxic Therapy` %>% filter(term == "pct_parp_inhibitor") %>% mutate(Classification = "TP53 CH"),
    msk_models_ch$`PPM1D CH Adjusted for Amount of Cytotoxic Therapy` %>% filter(term == "pct_parp_inhibitor") %>% mutate(Classification = "PPM1D CH")#,
    #msk_models_ch$`CHEK2 CH Adjusted for Amount of Cytotoxic Therapy` %>% filter(term == "pct_parp_inhibitor") %>% mutate(Classification = "CHEK2 CH")
) %>%
    mutate(
        term = case_when(
            term == "ind_parp_inhibitor" ~ "PARP Inhibitor\n(Adjusted for\nCytotoxic Therapy Class)",
            term == "pct_parp_inhibitor" ~ "PARP Inhibitor\n(Adjusted for\nAmount of Cytotoxic\nTherapy Recieved)"
        ),
        term = factor(term, levels = c("PARP Inhibitor\n(Adjusted for\nAmount of Cytotoxic\nTherapy Recieved)", "PARP Inhibitor\n(Adjusted for\nCytotoxic Therapy Class)")),
        Classification = factor(Classification, levels = c("DDR CH", "TP53 CH", "PPM1D CH", "CHEK2 CH")),
        p.label = ifelse(p.stars != "", paste0("P=",format(p.value, digits = 2)), "")
    ) %>%
    select(term, Classification, estimate, std.error, conf.low, conf.high, p.value, p.stars, p.label) %>%
    ggplot(
        aes(
            x = term,
            y = estimate,
            ymin = conf.low,
            ymax = conf.high,
            col = Classification,
            fill = Classification
        )
    ) +
    geom_point(position = position_dodge(width = 0.5), size = 5) +
    geom_errorbar(position = position_dodge(width = 0.5), width = 0.2, linewidth = 1) +
    #geom_text(aes_string(label = "p.stars", vjust = 0.1), size = 8, position = position_dodge(width = 0.5), color = "black") +
    geom_text(aes(label = p.label, vjust = -0.8), size = 4, position = position_dodge(width = 0.5), color = "black") +
    geom_hline(yintercept = 1, color = "black", linetype = "solid") +
    coord_flip() +
    scale_color_nejm() +
    #scale_color_manual(values = c("#316675", "#587a8a", "#8badbd")) +
    scale_y_log10(breaks = c(0.1, 0.2, 0.3, 0.5, 1, 2, 3, 5, 10)) +
    labs(
        y = "Odds Ratio of DDR CH",
        x = "",
        title = "",
        color = "Gene",
        fill = "Gene"
    ) +
    panel_theme_basic +
    theme(
        panel.grid.major.x = element_line(color = alpha("grey", 0.8), size = 0.5, linetype = "solid")
        #axis.text.x = ggtext::element_markdown(size = 17)
    )
supp_fig1b

supp_fig1 <- plot_grid(
    supp_fig1a,
    supp_fig1b,
    ncol = 2,
    align = "h",
    labels = c("a", "b"),
    label_size = 20
)
ggsave(paste0(figures_save_path, "SuppFigure1_Therapy_DDR_CH.png"), supp_fig1, width = 20, height = 10, units = "in", dpi = 300)
```

# Supp Figure 2 - Proportion of Patients and Drugs Prior to Study
```{r suppfig2_prior_drugs, message = FALSE, warning = FALSE}
# For each patient, find the earliest date for the specific drug regimen they were on
# This contains for each patient, the start of their drug regimen for our analysis
deid_earliest_regimen_date <- drug_info %>%
    filter(!(DEID %in% c(Not_Paired_DEID, Samples_Less_Than_30_Days_Apart))) %>%
    filter(druggeneric == Drug) %>%
    group_by(DEID, druggeneric, drugclass_c, Cohort, Drug) %>%
    summarise(earliest_regimen_date = min(APR_START_DTE, na.rm = TRUE), .groups = "drop")

# Treatment-naive in our definition is for patients who we have their sample at a specific regimen
# for example, carboplatin or PARPi, we want to see if they had any other "regimens" prior to their
# current regimen. So for example, if they are in the carboplatin cohort, we want to see if they 
# had any other drugs that were started prior to the start of their carboplatin regimen.
prior_drugs_df <- drug_info %>%
    filter(!(DEID %in% c(Not_Paired_DEID, Samples_Less_Than_30_Days_Apart))) %>%
    # We will also remove "oral" drugs that were only taken for a day since these are likely issues with data entry
    filter(!(grepl("oral", APR_ROUTE) & APR_DURATION == 1)) %>%
    # Now we need to find the oldest occurrence of a specific drug
    group_by(DEID, druggeneric, drugclass_c, Cohort) %>%
    summarise(earliest_drug_date = min(APR_START_DTE, na.rm = TRUE)) %>%
    left_join(
        deid_earliest_regimen_date %>%
            select(DEID, Cohort, earliest_regimen_date),
        by = c("DEID", "Cohort")
    ) %>%
    # These are all the drugs that were received prior to the earliest sample collection date, so we can be assured that they were received before the sample was collected
    filter(
        earliest_drug_date < (earliest_regimen_date)
    ) %>%
    mutate(
        drugclass = case_when(
            drugclass_c == "targeted_therapy_parp" ~ "PARP Inhibitor",
            drugclass_c == "cytotoxic_therapy" ~ "Cytotoxic Therapy",
            drugclass_c == "cytotoxic_therapy_platinum" ~ "Platinum Therapy",
            drugclass_c == "radionuclide" ~ "Radionuclide",
            drugclass_c == "radiation_therapy" ~ "Radiation Therapy",
            drugclass_c == "immune_therapy" ~ "Immune Therapy",
            #drugclass_c == "biologic_therapy" ~ "Biologic Therapy",
            #drugclass_c == "hormonal_therapy" ~ "Hormonal Therapy",
            #drugclass_c == "protein_kinase_inhibitor" ~ "Protein Kinase Inhibitor",
            #drugclass_c == "targeted_therapy" ~ "Targeted Therapy",
            TRUE ~ "Other Targeted Therapy"
        )
    ) %>%
    # This oral entry overlaps between Olaparib and Niraparib, so we will remove it since it is likely a data entry error
    filter(!(drugclass == "PARP Inhibitor" & Cohort == "PARPi" & DEID == "1567490"))

# Dtermine how many patients in our dataset received each major drug class
prior_drugs_prop <- prior_drugs_df %>%
    group_by(Cohort, drugclass) %>%
    summarise(
        n_patients = n_distinct(DEID),
        .groups = "drop"
    ) %>%
    complete(Cohort, drugclass, fill = list(n_patients = 0)) %>%
    left_join(
        # Get total patients per cohort
        drug_info %>%
            group_by(Cohort) %>%
            summarise(total_patients = n_distinct(DEID), .groups = "drop"),
        by = "Cohort"
    ) %>%
    mutate(
        proportion = n_patients / total_patients,
        percentage = round(proportion * 100, 1)
    ) %>%
    arrange(Cohort, desc(percentage))

supp_fig2 <- prior_drugs_prop %>% 
  ggplot(
        aes(
            x = drugclass,
            y = percentage,
            fill = Cohort
        )
    ) +
    geom_bar(color = "black", stat = "identity", position = position_dodge()) +
    labs(
        x = "",
        y = "Percentage of Patients with Prior Exposure",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    theme(
        legend.position = c(0.8, 0.7),
        legend.direction = "vertical",
        plot.margin = margin(1, 0, 0, 1, "cm"),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 16),
        axis.text.y = element_text(size = 16),
        axis.title.y = element_text(size = 18)
    ) +
    scale_y_continuous(labels = scales::percent_format(scale = 1), limits = c(0, 100), expand = c(0, 0), breaks = seq(0, 100, 10))
supp_fig2
ggsave(paste0(figures_save_path, "SuppFigure2_PriorDrugs.png"), supp_fig2, width = 10, height = 8, units = "in", dpi = 300)
```

# Supp Figure 3 - Carbo before PARP and PARP
```{r supp_fig3, message = FALSE, warning = FALSE}
carbo_then_parp <- drug_info %>%
    filter(original_data == TRUE) %>%
    filter(!(DEID %in% c(Not_Paired_DEID, Samples_Less_Than_30_Days_Apart))) %>%
    # We will also remove "oral" drugs that were only taken for a day since these are likely issues with data entry
    filter(!(grepl("oral", APR_ROUTE) & APR_DURATION == 1)) %>%
    # Now we need to find the oldest occurrence of a specific drug
    group_by(DEID, druggeneric, drugclass_c, Cohort) %>%
    summarise(earliest_drug_date = min(APR_START_DTE, na.rm = TRUE)) %>%
    left_join(
        deid_earliest_regimen_date %>%
            select(DEID, Cohort, earliest_regimen_date),
        by = c("DEID", "Cohort")
    ) %>%
    # These are all the drugs that were received prior to the earliest sample collection date, so we can be assured that they were received before the sample was collected
    filter(
        earliest_drug_date < (earliest_regimen_date)
    ) %>%
    mutate(
        drugclass = case_when(
            drugclass_c == "targeted_therapy_parp" ~ "PARP Inhibitor",
            drugclass_c == "cytotoxic_therapy" ~ "Cytotoxic Therapy",
            drugclass_c == "cytotoxic_therapy_platinum" ~ "Platinum Therapy",
            drugclass_c == "radionuclide" ~ "Radionuclide",
            drugclass_c == "radiation_therapy" ~ "Radiation Therapy",
            drugclass_c == "immune_therapy" ~ "Immune Therapy",
            TRUE ~ "Other Targeted Therapy"
        )
    ) %>%
    # This oral entry overlaps between Olaparib and Niraparib, so we will remove it since it is likely a data entry error
    filter(!(drugclass == "PARP Inhibitor" & Cohort == "PARPi" & DEID == "1567490")) %>%
    filter(Cohort == "PARPi", drugclass == "Platinum Therapy") %>%
    ungroup() %>%
    distinct(DEID) %>%
    pull(DEID)

carbo_then_carbo <- drug_info %>%
    filter(original_data == TRUE) %>%
    filter(!(DEID %in% c(Not_Paired_DEID, Samples_Less_Than_30_Days_Apart))) %>%
    # We will also remove "oral" drugs that were only taken for a day since these are likely issues with data entry
    filter(!(grepl("oral", APR_ROUTE) & APR_DURATION == 1)) %>%
    # Now we need to find the oldest occurrence of a specific drug
    group_by(DEID, druggeneric, drugclass_c, Cohort) %>%
    summarise(earliest_drug_date = min(APR_START_DTE, na.rm = TRUE)) %>%
    left_join(
        deid_earliest_regimen_date %>%
            select(DEID, Cohort, earliest_regimen_date),
        by = c("DEID", "Cohort")
    ) %>%
    # These are all the drugs that were received prior to the earliest sample collection date, so we can be assured that they were received before the sample was collected
    filter(
        earliest_drug_date < (earliest_regimen_date)
    ) %>%
    mutate(
        drugclass = case_when(
            drugclass_c == "targeted_therapy_parp" ~ "PARP Inhibitor",
            drugclass_c == "cytotoxic_therapy" ~ "Cytotoxic Therapy",
            drugclass_c == "cytotoxic_therapy_platinum" ~ "Platinum Therapy",
            drugclass_c == "radionuclide" ~ "Radionuclide",
            drugclass_c == "radiation_therapy" ~ "Radiation Therapy",
            drugclass_c == "immune_therapy" ~ "Immune Therapy",
            TRUE ~ "Other Targeted Therapy"
        )
    ) %>%
    # This oral entry overlaps between Olaparib and Niraparib, so we will remove it since it is likely a data entry error
    filter(!(drugclass == "PARP Inhibitor" & Cohort == "PARPi" & DEID == "1567490")) %>%
    filter(Cohort == "Carboplatin", drugclass == "Platinum Therapy") %>%
    ungroup() %>%
    distinct(DEID) %>%
    pull(DEID)

carbo_then_parp_tp <- rbind(
    timepoints %>%
        filter(DeID %in% carbo_then_parp),
    timepoints %>%
        filter(DeID %in% c("1536848", "1734282", "1755649", "1592606", "1620504")) %>%
        filter(Cohort == "PARPi")
) %>%
    mutate(
        multiple_drug_classification = "Received Carboplatin"
    ) %>%
    filter(Gene_Class == "DDR")

df_to_plot <- timepoints %>%
    filter(!(DeID %in% carbo_then_parp_tp$DeID)) %>%
    filter(Cohort == "PARPi") %>%
    mutate(
        multiple_drug_classification = "No Prior Carboplatin"
    ) %>%
    rbind(carbo_then_parp_tp) %>%
    rbind(
        timepoints %>%
            filter(!(DeID %in% carbo_then_parp_tp$DeID)) %>%
            filter(Cohort == "Carboplatin") %>%
            mutate(
                multiple_drug_classification = "Carboplatin"
            )
    ) %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(Gene_Class == "DDR") %>%
    mutate(
        multiple_drug_classification = factor(multiple_drug_classification, levels = c("Carboplatin", "No Prior Carboplatin", "Received Carboplatin"))
    )

model_ddr_carbo_then_parp <- rbind(
    glm(
        formula = growth_rate ~ multiple_drug_classification + AGE + SEX + RACE,
        data = df_to_plot
    ) %>% sjPlot::get_model_data(type = "est") %>% filter(grepl("multiple_drug_classification", term)),
    glm(
        formula = growth_rate ~ multiple_drug_classification + AGE + SEX + RACE,
        data = df_to_plot %>% filter(multiple_drug_classification != "Carboplatin")
    ) %>% sjPlot::get_model_data(type = "est") %>% filter(grepl("multiple_drug_classification", term))
)

supp_fig3 <- df_to_plot %>%
    ggplot(
        aes(
            x = multiple_drug_classification,
            y = growth_rate,
            fill = Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    labs(
        x = "",
        y = "Growth Rate of DDR Mutations",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = c("#0072B5FF", "#E18727FF", "#EAAB67FF")) +
    theme(
        legend.position = "top",
        plot.margin = margin(2, 0, 0, 1, "cm"),
        legend.text = element_text(size = 20),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16)
    ) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05), limits = c(NA,0.3)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 4, 1, 2, model_ddr_carbo_then_parp$p.value[1], model_ddr_carbo_then_parp$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 5, 1, 3, model_ddr_carbo_then_parp$p.value[2], model_ddr_carbo_then_parp$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 4.2, 2, 3, model_ddr_carbo_then_parp$p.value[3], model_ddr_carbo_then_parp$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6))
    #do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 4, 1, 1.8, model_ddr_carbo_then_parp$p.value[1], model_ddr_carbo_then_parp$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    #do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 5, 1, 2.2, model_ddr_carbo_then_parp$p.value[2], model_ddr_carbo_then_parp$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    #do.call(geom_signif, default_sig_data(df_to_plot %>% filter(Gene_Class == "DDR"), 4.2, 1.8, 2.2, model_ddr_carbo_then_parp$p.value[3], model_ddr_carbo_then_parp$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6))
supp_fig3
ggsave(paste0(figures_save_path, "SuppFigure3_CarboBeforePARP_GrowthRates.png"), supp_fig3, width = 12, height = 8, units = "in", dpi = 300)
```

# Supp Figure 4 - mCA Growth x CH Growth Rate
```{r supp_fig4, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
# There are 69 patients with mCA detected at either timepoint, and they also have a CH mutation detected at either timepoint
has_mca_and_ch <- intersect(
    mocha_timepoints$PatientID,
    timepoints$DeID
)

df_to_plot <- timepoints %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(!(DeID %in% c(parp_then_carbo, carbo_then_parp))) %>%
    filter(DeID %in% has_mca_and_ch) %>%
    filter(DeID != "PA00051248") %>%  # Outlier with no mCA or CH
    filter(Gene_Class == "DDR" | Gene_Class == "DTA") %>%
    select(DeID, Cohort, change_in_VAF, growth_rate) %>%
    dplyr::rename(PatientID = DeID) %>%
    group_by(PatientID, Cohort) %>%
    summarise(
        average_change_in_VAF = mean(change_in_VAF, na.rm = TRUE),
        average_CH_growth_rate = mean(growth_rate, na.rm = TRUE)
    ) %>%
    left_join(
        mocha_timepoints %>%
            filter(growth_rate != Inf & growth_rate != -Inf) %>%
            filter(!(PatientID %in% c(parp_then_carbo, carbo_then_parp))) %>%
            filter(PatientID %in% has_mca_and_ch) %>%
            filter(event == "mCA") %>%
            select(PatientID, Cohort, change_in_cf, growth_rate) %>%
            group_by(PatientID, Cohort) %>%
            summarise(
                average_change_in_cf = mean(change_in_cf, na.rm = TRUE),
                average_mCA_growth_rate = mean(growth_rate, na.rm = TRUE)
            ),
        by = c("PatientID", "Cohort")
    )

# By Growth Rate
supp_fig4 <- df_to_plot %>%
    ggplot(
        aes(
            x = average_CH_growth_rate,
            y = average_mCA_growth_rate,
            color = Cohort
        )
    ) +
    geom_point(size = 3) +
    labs(
        x = "Average CH Growth Rate",
        y = "Average mCA Growth Rate",
        color = "Cohort"
    ) +
    panel_theme_basic +
    scale_color_nejm() +
    theme(
        legend.position = "right",
        legend.direction = "vertical",
        plot.margin = margin(1, 0, 1, 1, "cm")
    ) +
    geom_smooth(method = "lm", se = FALSE)
supp_fig4
ggsave(paste0(figures_save_path, "SuppFigure4_CHvsCNA_GrowthRate.png"), supp_fig4, width = 10, height = 8, units = "in", dpi = 300)
```

# Supp Figure 5B - CD45 Isoforms
```{r supp_fig5b, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
supp_fig5b <- make_mouse_cell_plot(
    mouse_data[["SuppFigure 5B"]] %>%
        mutate(Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib"))),
    cell_col = "WT:WT Total Leukocytes",
    title = "WT:WT Total Leukocytes", y_lab = "CD45.2 Cells\n(Normalized to 0-Week)"
)
supp_fig5b
ggsave(paste0(figures_save_path, "SuppFigure5B_CD45_Isoforms.png"), supp_fig5b, width = 10, height = 8, units = "in", dpi = 300)
```

# Supp Figure 6 - Leukocytes Raw Chimerism
```{r supp_fig_leukocytes_raw_chimerism, message = FALSE, warning = FALSE, fig.width=10, fig.height=6}
supp_fig6 <- mouse_data[["SuppFigure 6"]] %>%
    mutate(Cohort = factor(Cohort, levels = c("Vehicle", "Cisplatin", "Talazoparib", "Olaparib"))) %>%
    group_by(Cohort, Week) %>%
    summarise(
      mean_value = mean(Leukocytes, na.rm = TRUE),
      sd_value = sd(Leukocytes, na.rm = TRUE),
      sem_value = sd(Leukocytes, na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    ) %>%
    ggplot(
      aes(
        x = factor(Week),
        y = mean_value,
        fill = Cohort,
        color = Cohort,
        shape = Cohort,
        group = Cohort
      )
    ) +
    geom_point(size = 4) +
    geom_line() +
    geom_errorbar(
      aes(
        ymin = mean_value - sem_value,
        ymax = mean_value + sem_value
      ),
      width = 0.5
    ) +
    labs(
      x = "Weeks Post-Treatment",
      y = "%CD45.2 Cells",
      title = "Leukocytes",
      fill = "Cohort",
      color = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_nejm() +
    scale_color_nejm() +
    scale_shape_manual(values = c(15, 16, 17, 18)) +
    scale_y_continuous(limits = c(0, 80), labels = scales::label_number(accuracy = 1L)) +
    theme(
      legend.position = "right",
      legend.direction = "vertical",
      plot.margin = margin(1, 1, 1, 1, "cm"),
      plot.title = element_text(hjust = 0.5)
    ) +
    scale_x_discrete(limits = as.character(0:20), expand = c(0, 0.5), breaks = c(0, 6, 10, 14, 18))
supp_fig6 <- add_significance_annotation(supp_fig6, "P=0.0018", 19.5, 67, 40, size_text = 4)
ggsave(paste0(figures_save_path, "SuppFigure6_Leukocytes_Raw_Chimerism.png"), supp_fig6, width = 12, height = 6, units = "in", dpi = 300)
```


# Supp Figure 7 - CH Growth Rate by Germline HRD Status
```{r suppfig7_growth_rate_germline_HRD, message = FALSE, warning = FALSE}
df_to_plot <- timepoints %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>%
    filter(Gene_Class == "DDR" | Gene_Class == "DTA") %>%
    mutate(
        BRCA = case_when(
            HRD_Single %in% c("BRCA1", "BRCA2") ~ "BRCA1/2",
            HRD_Single %in% c("ATM", "CHEK2", "RAD51D", "BRIP1") ~ "Other HRD Germline",  # Keep these as-is
            TRUE ~ as.character(HRD_Single)  # Keep all other values as-is
        ),
        BRCA = ifelse(is.na(BRCA), "Other HRD Germline", BRCA)  # Replace NA with "BRIP1" because only 1 patient is missing
    ) %>%
    filter(BRCA %in% c("No Germline", "BRCA1/2", "Other HRD Germline"))

model_growth_rate_germline_BRCA_class_glm <- purrr::cross_df(list(
    class = c("DDR"),
    germline = c("No Germline", "BRCA1/2", "Other HRD Germline")
)) %>%
    pmap_dfr(function(class, germline) {
        print(paste("Processing", class, germline))
        main <- if (germline != "No Germline") {
            glm(
                formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                data = df_to_plot %>%
                    filter(Gene_Class == class, BRCA == germline) %>%
                    filter(Cohort != "Healthy") %>%
                    mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi")))
            ) %>%
                sjPlot::get_model_data(type = "est") %>%
                filter(grepl("Cohort", term)) %>%
                mutate(
                    Class = class, 
                    BRCA = germline,
                    term = "CarboplatinVSPARPi"
                )
        } else {
            bind_rows(
                glm(
                    formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                    data = df_to_plot %>%
                        filter(Gene_Class == class, BRCA == germline)
                ) %>%
                    sjPlot::get_model_data(type = "est") %>%
                    filter(grepl("Cohort", term)) %>%
                    mutate(
                        Class = class, 
                        BRCA = germline,
                        term = case_when(
                            term == "CohortCarboplatin" ~ "NoTreatmentVSCarboplatin",
                            term == "CohortPARPi" ~ "NoTreatmentVSPARPi"
                        )
                    ),
                glm(
                    formula = growth_rate ~ Cohort + AGE + SEX + RACE,
                    data = df_to_plot %>%
                        filter(Gene_Class == class, BRCA == germline) %>%
                        filter(Cohort != "Healthy") %>%
                        mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi")))
                ) %>%
                    sjPlot::get_model_data(type = "est") %>%
                    filter(grepl("Cohort", term)) %>%
                    mutate(
                        Class = class, 
                        BRCA = germline,
                        term = "CarboplatinVSPARPi"
                    )
            )
        }
    })
# Add the BRCA effect for each class and cohort
brca_effect <- map_dfr(c("Carboplatin", "PARPi"), function(cohort) {
    rbind(
        glm(
        formula = growth_rate ~ BRCA + AGE + SEX + RACE,
        data = df_to_plot %>%
            filter(Gene_Class == "DDR") %>%
            filter(Cohort == cohort) %>%
            mutate(BRCA = factor(BRCA, levels = c("No Germline", "BRCA1/2", "Other HRD Germline")))
    ) %>%
        sjPlot::get_model_data(type = "est") %>%
        filter(grepl("BRCA", term)) %>%
        mutate(
            term = case_when(
                term == "BRCABRCA1/2" ~ "NoGermlineVSBRCA1/2",
                term == "BRCAOther HRD Germline" ~ "NoGermlineVSOtherHRD"
            ),
            Class = "DDR",
            BRCA = cohort
        ),
        glm(
            formula = growth_rate ~ BRCA + AGE + SEX + RACE,
            data = df_to_plot %>%
                filter(Gene_Class == "DDR") %>%
                filter(Cohort == cohort) %>%
                filter(BRCA != "No Germline") %>%
                mutate(BRCA = factor(BRCA, levels = c("BRCA1/2", "Other HRD Germline")))
        ) %>%
        sjPlot::get_model_data(type = "est") %>%
        filter(term == "BRCAOther HRD Germline") %>%
        mutate(
            term = "BRCA1/2VsOtherHRD",
            Class = "DDR",
            BRCA = cohort
        )
    )
})
model_growth_rate_germline_BRCA_class_glm <- bind_rows(model_growth_rate_germline_BRCA_class_glm, brca_effect)
model_growth_rate_germline_BRCA_class_glm <- model_growth_rate_germline_BRCA_class_glm %>% filter(Class == "DDR")

glm(
    formula = growth_rate ~ BRCA + AGE + SEX + RACE,
    data = df_to_plot %>%
        filter(Gene_Class == "DDR") %>%
        filter(Cohort == "PARPi") %>%
        filter(BRCA != "No Germline") %>%
        mutate(BRCA = factor(BRCA, levels = c("BRCA1/2", "Other HRD Germline")))
) %>%
sjPlot::get_model_data(type = "est")

df_to_plot <- df_to_plot %>%
    filter(BRCA %in% c("No Germline", "BRCA1/2", "Other HRD Germline")) %>%
    filter(growth_rate != Inf & growth_rate != -Inf) %>% 
    filter(Gene_Class == "DDR") %>%
    mutate(BRCA = factor(BRCA, levels = c("No Germline", "BRCA1/2", "Other HRD Germline", "Other Germline")))
supp_fig7 <- df_to_plot %>%
    ggplot(
        aes(
            x = BRCA,
            y = growth_rate,
            fill = Cohort
        )
    ) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_manual(values = treatment_colors) +
    theme(plot.margin = margin(2, 0, 0, 1, "cm")) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), limit = c(NA, 4), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 4, 0.75, 1, model_growth_rate_germline_BRCA_class_glm$p.value[1], model_growth_rate_germline_BRCA_class_glm$p.stars[1], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 5, 0.75, 1.25, model_growth_rate_germline_BRCA_class_glm$p.value[2], model_growth_rate_germline_BRCA_class_glm$p.stars[2], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 6, 1, 1.25, model_growth_rate_germline_BRCA_class_glm$p.value[3], model_growth_rate_germline_BRCA_class_glm$p.stars[3], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 4, 1.81, 2.19, model_growth_rate_germline_BRCA_class_glm$p.value[4], model_growth_rate_germline_BRCA_class_glm$p.stars[4], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 3, 2.81, 3.19, model_growth_rate_germline_BRCA_class_glm$p.value[5], model_growth_rate_germline_BRCA_class_glm$p.stars[5], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 4.5, 1, 1.81, model_growth_rate_germline_BRCA_class_glm$p.value[6], model_growth_rate_germline_BRCA_class_glm$p.stars[6], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 7, 1, 2.81, model_growth_rate_germline_BRCA_class_glm$p.value[7], model_growth_rate_germline_BRCA_class_glm$p.stars[7], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 5, 1.81, 2.81, model_growth_rate_germline_BRCA_class_glm$p.value[8], model_growth_rate_germline_BRCA_class_glm$p.stars[8], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 6, 1.25, 2.19, model_growth_rate_germline_BRCA_class_glm$p.value[9], model_growth_rate_germline_BRCA_class_glm$p.stars[9], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 8, 1.25, 3.19, model_growth_rate_germline_BRCA_class_glm$p.value[10], model_growth_rate_germline_BRCA_class_glm$p.stars[10], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6)) +
    do.call(geom_signif, default_sig_data(df_to_plot, 4, 2.19, 3.19, model_growth_rate_germline_BRCA_class_glm$p.value[11], model_growth_rate_germline_BRCA_class_glm$p.stars[11], show_values = TRUE, hide_ns = TRUE, size = 0.5, textsize = 6))
supp_fig7
ggsave(paste0(figures_save_path, "SuppFigure7_GrowthRate_HRD_Germline.png"), supp_fig7, width = 12, height = 8, units = "in", dpi = 300)
```

# Supp Figure 10 - No Rescue
```{r supp_fig10, message = FALSE, warning = FALSE, fig.width=15, fig.height=20}
df_to_plot <- timepoints %>%
  filter(growth_rate_sensitivity != Inf & growth_rate_sensitivity != -Inf) %>%
  filter(Gene_Class == "DDR" | Gene_Class == "DTA")

model_growth_rate_gene_class_sensitivity <- rbind(
    glm(
        formula = growth_rate_sensitivity ~ Cohort + AGE + SEX + RACE,
        data = df_to_plot %>% filter(Gene_Class == "DDR")
    ) %>%
        sjPlot::get_model_data(type = "est") %>%
        filter(grepl("Cohort", term)),
    glm(
        formula = growth_rate_sensitivity ~ Cohort + AGE + SEX + RACE,
        data = df_to_plot %>% filter(Gene_Class == "DDR") %>%
            filter(Cohort != "Healthy") %>%
            mutate(Cohort = factor(Cohort, levels = c("Carboplatin", "PARPi")))
    ) %>%
        sjPlot::get_model_data(type = "est") %>%
        filter(grepl("Cohort", term)) %>%
        mutate(term = "CarboplatinPARPi")
)

counts <- df_to_plot %>%
    group_by(Cohort, Gene_Class) %>%
    summarise(n = n(), .groups = "drop")

supp_fig10 <- df_to_plot %>%
    ggplot(
        aes(
            x = Gene_Class,
            y = growth_rate_sensitivity,
            fill = Cohort 
        )
    ) +
    geom_boxplot(outlier.shape = NA) +
    geom_point(position = position_jitterdodge(jitter.width=0.2), alpha = 0.2, color = "black") +
    geom_text(data = counts, aes(label = n, y = 0.04), size = 8, position = position_dodge(width = 0.8)) +
    geom_hline(yintercept = 0, color = "black", alpha = 0.3) +
    labs(
        x = "",
        y = "Growth Rate",
        fill = "Cohort"
    ) +
    panel_theme_basic +
    scale_fill_nejm() + 
    theme(plot.margin = margin(1, 0, 0, 1, "cm")) +
    scale_y_continuous(trans = scales::pseudo_log_trans(0.001), breaks = c(-0.05, -0.01, -0.005, 0, 0.005, 0.01, 0.05), limit = c(NA, 1.5)) +
    do.call(geom_signif, default_sig(5.0, 0.75, 1, model_growth_rate_gene_class_sensitivity$p.value[1], model_growth_rate_gene_class_sensitivity$p.stars[1], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(5.6, 0.75, 1.25, model_growth_rate_gene_class_sensitivity$p.value[2], model_growth_rate_gene_class_sensitivity$p.stars[2], show_values = TRUE, hide_ns = TRUE, textsize = 6)) +
    do.call(geom_signif, default_sig(6.4, 1, 1.25, model_growth_rate_gene_class_sensitivity$p.value[3], model_growth_rate_gene_class_sensitivity$p.stars[3], show_values = TRUE, hide_ns = TRUE, textsize = 6))
supp_fig10
ggsave(paste0(figures_save_path, "SuppFigure10_No_Rescue_GrowthRate_Sensitivity.png"), supp_fig10, width = 10, height = 8, units = "in", dpi = 300)
```

# Supplementary Table 1 - MSK Demographics
```{r msk_table}
label(msk_df$age) <- "Age at Treatment Start"
label(msk_df$race) <- "Race"
label(msk_df$SystemTumorType) <- "Cancer Diagnosis"
label(msk_df$smoke_bin) <- "Smoking Status"

table1(~ age + Gender + race + smoke_bin + SystemTumorType | Treatment, data = msk_df)
```

# Supplementary Table 2 - MSK Clonal Hematopoiesis
```{r msk_clinical, echo=FALSE, message = FALSE, warning = FALSE}
label(msk_df$ch_pancan_pd_bin) <- "Clonal Hematopoiesis"
label(msk_df$mutnum_pancan_pd) <- "Number of Mutations"
label(msk_df$VAF_pancan_pd) <- "Maximum VAF"

table1(
  ~ ch_pancan_pd_bin + VAF_pancan_pd + mutnum_pancan_pd | Treatment, 
  data = msk_df
)
```

# Supplementary Table 3 - Carboplatin and PARPi Demographics
```{r carbo_parp_table, echo=FALSE, message = FALSE, warning = FALSE}
label(table_demographics$AGE) <- "Age at Treatment Start"
label(table_demographics$HRD) <- "Germline Genetic Testing"
label(table_demographics$CANCER.DX) <- "Cancer Diagnosis"
label(table_demographics$RACE) <- "Race"
label(table_demographics$SEX) <- "Sex"

table1(~ AGE + SEX + RACE + Smoking + Drug + CANCER.DX + HRD + HRD_Single | Cohort, data = table_demographics %>% mutate(Cohort = factor(Cohort, levels = c("Healthy", "Carboplatin", "PARPi"))))
```

# Supplementary Table 4 - Longitudinal CH Mutations
```{r ch_mutation_table, echo=FALSE, message = FALSE, warning = FALSE}
timepoints %>%
    select(key, Gene) %>% 
    mutate(Gene = factor(Gene, levels = gene_list)) %>%
    distinct() %>%
    arrange(Gene) %>%
    fwrite(paste0(figures_save_path, "SuppTable4_Longitudinal_CH_Mutations.csv"))
```

# Supplementary Table 5 - CH Mutations with Mutational Characteristics
```{r ch_mutation_characteristics, echo=FALSE, message = FALSE, warning = FALSE}
timepoints %>%
    select(DeID, Cohort, key, Gene, preVAF, postVAF, change_in_days) %>%
    mutate(Gene = factor(Gene, levels = gene_list)) %>%
    arrange(Gene) %>%
    dplyr::rename(
        `VAF at Pre-Treatment` = preVAF,
        `VAF at Post-Treatment` = postVAF,
        `Days Between Timepoints` = change_in_days
    ) %>%
    fwrite(paste0(figures_save_path, "SuppTable5_CH_Mutations_Characteristics.csv"))
```

# Supplementary Table 6 - Prior Drugs
```{r prior_drugs_table, echo=FALSE, message = FALSE, warning = FALSE}
drug_info %>%
    filter(!(DEID %in% c(Not_Paired_DEID, Samples_Less_Than_30_Days_Apart))) %>%
    # We will also remove "oral" drugs that were only taken for a day since these are likely issues with data entry
    filter(!(grepl("oral", APR_ROUTE) & APR_DURATION == 1)) %>%
    # Now we need to find the oldest occurrence of a specific drug
    group_by(DEID, druggeneric, drugclass_c, Cohort) %>%
    summarise(earliest_drug_date = min(APR_START_DTE, na.rm = TRUE)) %>%
    left_join(
        deid_earliest_regimen_date %>%
            select(DEID, Cohort, earliest_regimen_date),
        by = c("DEID", "Cohort")
    ) %>%
    # These are all the drugs that were received prior to the earliest sample collection date, so we can be assured that they were received before the sample was collected
    filter(
        earliest_drug_date < (earliest_regimen_date)
    ) %>%
    mutate(
        drugclass = case_when(
            drugclass_c == "targeted_therapy_parp" ~ "PARP Inhibitor",
            drugclass_c == "cytotoxic_therapy" ~ "Cytotoxic Therapy",
            drugclass_c == "cytotoxic_therapy_platinum" ~ "Platinum Therapy",
            drugclass_c == "radionuclide" ~ "Radionuclide",
            drugclass_c == "radiation_therapy" ~ "Radiation Therapy",
            drugclass_c == "immune_therapy" ~ "Immune Therapy",
            #drugclass_c == "biologic_therapy" ~ "Biologic Therapy",
            #drugclass_c == "hormonal_therapy" ~ "Hormonal Therapy",
            #drugclass_c == "protein_kinase_inhibitor" ~ "Protein Kinase Inhibitor",
            #drugclass_c == "targeted_therapy" ~ "Targeted Therapy",
            TRUE ~ "Other Targeted Therapy"
        )
    ) %>%
    # This oral entry overlaps between Olaparib and Niraparib, so we will remove it since it is likely a data entry error
    filter(!(drugclass == "PARP Inhibitor" & Cohort == "PARPi" & DEID == "1567490")) %>%
    ungroup() %>%
    select(DEID, druggeneric, drugclass) %>%
    pivot_wider(names_from = drugclass, values_from = druggeneric, values_fn = list(druggeneric = function(x) paste(unique(x), collapse = "; ")), values_fill = "") %>%
    fwrite(paste0(figures_save_path, "SuppTable6_Patients_Prior_Drugs.csv"))
```

# Supplementary Table 7 - MoChA Demographics
```{r mocha_table, echo=FALSE, message = FALSE, warning = FALSE}
label(mocha_demographics$AGE) <- "Age at Treatment Start"
label(mocha_demographics$Sex_Reported) <- "Sex"
label(mocha_demographics$Ancestry) <- "Race"

# Certain DeIDs are in both Carboplatin and PARPi cohorts, so we need to assign 
# them to one or the other based on their earliest AGE at treatment start
multi_cohort_deid_map <- c(
  "1108236" = "PARPi",
  "1536848" = "Carboplatin",
  "1537527" = "PARPi",
  "1592606" = "Carboplatin",
  "1592759" = "PARPi",
  "1620504" = "Carboplatin",
  "1734282" = "Carboplatin",
  "1755649" = "Carboplatin",
  "1782310" = "PARPi"
)

table1(
 ~ AGE + Sex_Reported + Ancestry | Cohort, 
 data = mocha_demographics %>%
      arrange(AGE) %>%                        # We assume the earliest AGE is the FIRST sample
      mutate(Cohort = dplyr::coalesce(multi_cohort_deid_map[as.character(DeID)], Cohort)) %>%
      distinct(DeID, Cohort, .keep_all = TRUE) %>%
      filter(Cohort != "")
)
```